---
title: "Predicting drug mode of action: loading data and preselecting features"
author: "Florian Huber, Léonard Dubois"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

# Setup, library loading

```{r}
knitr::opts_chunk$set(echo = T)
knitr::opts_chunk$set(message = T)
knitr::opts_chunk$set(warning = F)
knitr::opts_chunk$set(error = T)
knitr::opts_chunk$set(cache = T)
Sys.setlocale("LC_ALL", "en_IE.UTF-8")

library(tidyverse)
library(mlr)

walk(list.files("./R", pattern = "*.R", full.names = T), source)
```


# Loading and merging data

## Read in tables, join them

```{r}
nichols_2011 <- read.table("/Volumes/typas/Florian/dbsetup_tables/nichols_2011.csv", header = T, 
                           sep = ";", stringsAsFactors = F)
strains <- read.table("/Volumes/typas/Florian/dbsetup_tables/strains.csv", header = T, 
                           sep = ";", stringsAsFactors = F)
strains_has_genes <- read.table("/Volumes/typas/Florian/dbsetup_tables/strains_has_genes.csv", 
                                header = T, sep = ";", stringsAsFactors = F)
genes <- read.table("/Volumes/typas/Florian/dbsetup_tables/genes.csv", header = T, sep = ";", 
                    stringsAsFactors = F)
# KNIME table
drugs_full <- read.table("/Volumes/typas/Florian/dbsetup_tables/drugs_full.csv", header = T, 
                         sep = ";", stringsAsFactors = F, dec = ",")
drugs_full$X <- NULL
mode_of_action <- read.table("/Volumes/typas/Florian/dbsetup_tables/mode_of_action.csv", 
                             header = T, sep = ";", stringsAsFactors = F)
```

Add gene information to Nichols table, remove unnecessary columns.

```{r}
the_matrix <- 
   nichols_2011 %>%
   left_join(strains[, c("strain"), drop = F]) %>%
   left_join(strains_has_genes[, c("strain", "ugi")]) %>%
   left_join(genes[, c("ugi", "gene_synonym")]) %>%
   select(gene_synonym, drugname_typaslab, conc, sscore, qvalue, strain)

the_matrix$significant <- the_matrix$qvalue <= 0.05
```

Join drug tables with mode of action information. We only keep drugs which target 'cell_wall', 
'dna', 'protein_synthesis' and 'membrane_stress' because the other MoAs don't have enough class 
members for predictions. Exclude the respective drugs from `the_matrix`. 

```{r}
moas_to_keep <- c("cell_wall", "dna", "protein_synthesis", "membrane_stress")

drugs_full <- left_join(drugs_full, mode_of_action[, c("moa_id", "process_broad")]) %>%
   select(-moa_id) %>% 
   filter(process_broad %in% moas_to_keep)

the_matrix <- filter(the_matrix, drugname_typaslab %in% drugs_full$drugname_typaslab)
```

For essential genes there were sometimes several hypomorphic mutants. We just want to keep one of 
them: the one with most phenotypes over all conditions.

```{r}
the_matrix <- 
   group_by(the_matrix, gene_synonym) %>%
   do(select_mutant(.))

tmp <- group_by(the_matrix, gene_synonym) %>% 
   mutate(n = length(unique(strain)))
stopifnot(all(tmp$n == 1))
```


Select drug dosages: if one of the dosages is significant, keep that one, if none or all are, keep 
the highest dosage. 

```{r}
the_matrix <- the_matrix %>%
   group_by(gene_synonym, drugname_typaslab) %>%
   do(select_dosage(.)) %>%
   ungroup()
```

If a gene doesn't interact with any drug, exclude it.

```{r}
the_matrix <- the_matrix %>%
   group_by(gene_synonym) %>% 
   mutate(significant_any = any(significant)) %>%
   ungroup()

the_matrix <- the_matrix[the_matrix$significant_any, ]
```

This leaves us with `r length(unique(the_matrix$gene_synonym))` genes. Only a very small fraction 
of gene drug combinations are missing (less than 0.1%):

```{r}
t <- table(the_matrix$gene_synonym, the_matrix$drugname_typaslab)
stopifnot(all(t < 2))
sum(t == 0) / sum(t < 2)
```

Now we can start constructing the final matrix. 

```{r}
the_matrix <- select(the_matrix, gene_synonym, drugname_typaslab, sscore)
the_matrix <- spread(the_matrix, key = gene_synonym, value = sscore)
```

We replace all NA values with the median of all s-scores over all conditions for a particular 
mutant. 

```{r}
# check if all drug names are defined 
stopifnot(!any(is.na(the_matrix$drugname_typaslab)))
sel <- grep(colnames(the_matrix), pattern = "drugname_typaslab")

the_matrix[, -sel] <- lapply(the_matrix[, -sel], function(x) {
   x[is.na(x)] <- median(x, na.rm = T)
   return(x)
})

if (any(sapply(the_matrix, is.na))) {
   stop("Undefined values present in the_matrix.")
}
```

Merge `the_matrix` with drug features. Make table `labels` containing the correct MoA 
classifications. 

```{r}
stopifnot(all(the_matrix$drugname_typaslab %in% drugs_full$drugname_typaslab))

drugs_full_selected_features <- drugs_full[, c("drugname_typaslab", "SlogP", "LabuteASA", "TPSA", 
                                               "ExactMW", "NumLipinskiHBA", "NumLipinskiHBD", 
                                               "NumRotatableBonds", "NumAmideBonds", "NumHeteroAtoms", 
                                               "NumHeavyAtoms", "NumAtoms", "NumStereocenters", 
                                               "NumUnspecifiedStereocenters", "NumRings", 
                                               "NumAromaticRings", "NumSaturatedRings", 
                                               "NumAliphaticRings", "data_effective_rotor_count")]

the_matrix <- left_join(the_matrix, drugs_full_selected_features)

labels <- drugs_full[, c("drugname_typaslab", "process_broad")]
```

Done. 

```{r}
save("the_matrix", file = "the_matrix.RData")
```


## Do further feature preselection (ANOVA, sorting by variance, ...)
...



# System and session info

```{r}
R.version
sessionInfo()
```

