---
title: "Predicting drug mode of action: loading data and preselecting features"
author: "Florian Huber, Leonard Dubois"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

# Setup, library loading

```{r}
rm(list = ls())
# function to check if a package is installed, if so, load it, else install and then load it
source("./R/ipak.R")
# set chunk options and load libraries
source("./setup.R")
```


# Loading and merging data

In all subsequent cases, the final goal is to have a matrix with the drugs in the rows and the 
features in the columns. We will refer to such a matrix as a `drug_feature_matrix`. In the next 
section we will generate different "versions" of this matrix, differing, for example, in the number 
of drugs or features selected or whether features were transformed in some way.


## Reading in and joining of tables, common preprocessing operations

```{r}
nichols_2011 <- read.table("/Volumes/typas/Florian/dbsetup_tables/nichols_2011.csv", header = T, 
                           sep = ";", stringsAsFactors = F)
strains <- read.table("/Volumes/typas/Florian/dbsetup_tables/strains.csv", header = T, 
                           sep = ";", stringsAsFactors = F)
strains_has_genes <- read.table("/Volumes/typas/Florian/dbsetup_tables/strains_has_genes.csv", 
                                header = T, sep = ";", stringsAsFactors = F)
genes <- read.table("/Volumes/typas/Florian/dbsetup_tables/genes.csv", header = T, sep = ";", 
                    stringsAsFactors = F)
# generated in project dbsetup using KNIME
drugs_full <- read.table("/Volumes/typas/Florian/dbsetup_tables/drugs.csv", header = T, 
                         sep = ";", stringsAsFactors = F, dec = ".")
drugs_full$X <- NULL
mode_of_action <- read.table("/Volumes/typas/Florian/dbsetup_tables/mode_of_action.csv", 
                             header = T, sep = ";", stringsAsFactors = F)
```

Add gene information to Nichols table, remove unnecessary columns.

```{r}
the_matrix <- 
   nichols_2011 %>%
   left_join(strains[, c("strain"), drop = F]) %>%
   left_join(strains_has_genes[, c("strain", "ugi")]) %>%
   left_join(genes[, c("ugi", "gene_synonym")]) %>%
   select(gene_synonym, drugname_typaslab, conc, sscore, qvalue, strain) 
    
the_matrix$significant <- the_matrix$qvalue <= 0.05
```

Join drug tables with mode of action information. 

drug_moa table on Google docs has 89 drugs. 

Of those 89 drugs there are missing in `drugs_full`: epinephrine, norepinephrine, glufosfomycin, UV, 
bile. 

In `the_matrix` there are missing EGCG, epinephrine, norepinephrine. 

So by keeping only the drugs in the_matrix which are also in `drugs_full` we lose 6 drugs (EGCG, 
epinephrine, norepinoephrine, glufosfomycin, UV, bile) and are left with 83 drugs. 

```{r}
drugs_full <- left_join(drugs_full, mode_of_action[, c("moa_id", "process_broad")]) %>%
   select(-moa_id)

saveRDS(drugs_full, file = "./data/programmatic_output/drugs_full.rds")

# exclude drugs that are not drugs_full - as those don't have chemical features
the_matrix <- filter(the_matrix, drugname_typaslab %in% drugs_full$drugname_typaslab)
```

We save this as `the_matrix_complete_nochanges`:

```{r}
saveRDS(the_matrix, file = "./data/programmatic_output/the_matrix_complete_nochanges.rds")
```

If a gene doesn't interact with any drug, exclude it. This reduces the number of genes from 3921 to 
1711. 

```{r}
the_matrix <- the_matrix %>%
   group_by(gene_synonym) %>% 
   filter(any(significant)) %>%
   ungroup()
```

This leaves us with `r length(unique(the_matrix$gene_synonym))` genes. Only a very small fraction 
of gene drug combinations are missing (less than 0.1%):

```{r}
t <- table(the_matrix$gene_synonym, the_matrix$drugname_typaslab)
sum(t == 0) / (nrow(t) * ncol(t))
```

For essential genes there were sometimes several hypomorphic mutants. We just want to keep one of 
them: always the one with most phenotypes over all conditions.

We will save this as `the_matrix_complete_strainsgenesremoved.rds`. This is the the_matrix version 
with (almost) all drugs and after hypomorphic mutant selection and removing genes not interacting 
with anything. Still possible to characterise the data set completely, change NA imputation, dosage 
selection, drug selection procedure. 

```{r}
the_matrix <- 
   group_by(the_matrix, gene_synonym) %>%
   do(select_mutant(.))

saveRDS(the_matrix, file = "./data/programmatic_output/the_matrix_complete_strainsgenesremoved.rds")

tmp <- group_by(the_matrix, gene_synonym) %>% 
   mutate(n = length(unique(strain))) %>%
   ungroup() %>%
   select(n)
stopifnot(all(tmp$n == 1))
rm(tmp)
```

Restructure the matrix to put drugs into rows, genes into columns. 

```{r}
# we need a matrix just indicating the significant s-scores for later on
the_matrix_signifs <- the_matrix

the_matrix <- select(the_matrix, gene_synonym, drugname_typaslab, conc, sscore)
the_matrix <- spread(the_matrix, key = gene_synonym, value = sscore)

the_matrix_signifs <- select(the_matrix_signifs, gene_synonym, drugname_typaslab, conc, significant)
the_matrix_signifs <- spread(the_matrix_signifs, key = gene_synonym, value = significant, fill = FALSE)
```


### Imputing NA values

We replace all NA values with the median of all s-scores over all conditions for a particular 
mutant. 

```{r}
# check if all drug names are defined 
stopifnot(!any(is.na(the_matrix$drugname_typaslab)))

sel <- grep(colnames(the_matrix), pattern = "drugname_typaslab|conc")
the_matrix[, -sel] <- lapply(the_matrix[, -sel], function(x) {
   x[is.na(x)] <- median(x, na.rm = T)
   return(x)
})

if (any(sapply(the_matrix, is.na))) {
   stop("Undefined values present in the_matrix.")
}
```

We save again this version of the matrix:

```{r}
saveRDS(the_matrix, file = "./data/programmatic_output/the_matrix_complete_strainsgenesremoved_NAsimputed_wideformat.rds")
```


# Generating different 'versions' of our matrix

## Drug selection and drug classification procedures

### Dosage selection

#### Approach 1: "`most_interactions`" 
Selects for each drug the one dosages with the highest number of significant interactions. If none 
or all are, keep the highest dosage. 

```{r}
selector <- 
   the_matrix_signifs %>%
   group_by(drugname_typaslab) %>%
   arrange(conc, .by_group = TRUE) %>%
   do(select_dosage_most_ias(.)) %>%
   ungroup() %>%
   pull(selector)

the_matrix <- the_matrix %>%
   group_by(drugname_typaslab) %>%
   arrange(conc, .by_group = TRUE) %>%
   ungroup()

the_matrix_alldosgs_nochemfeats <- the_matrix
the_matrix_mostias_nochemfeats <- the_matrix[selector, ]
```


## Collecting data in a data frame with list columns - matrix_container

```{r}
matrix_container <- 
   tibble(datasets_included = list("nichols_2011", "nichols_2011"), 
          drug_dosages = c("all", "most_interactions"), 
          feat_preselect = c("keepall", "keepall"), 
          chemical_feats = c(FALSE, FALSE), 
          drug_feature_matrices = list(the_matrix_alldosgs_nochemfeats, the_matrix_mostias_nochemfeats))
```


## Feature selection and transformation procedures

### Selecting features with the highest variance

Sort features (i.e. mutants = genes here) by variance and select top x %. 

```{r}
variances_to_select <- c(5, 10, 15, 20, 25, 30, 40, 50)

# add some datasets to our matrix_container: for the table using all dosages, we want to select 
# the genes which have the highest variance (top x%)
targetrow <- match("all", matrix_container$drug_dosages)
for (v in variances_to_select) {
   tmp_row <- matrix_container[targetrow, ] # = row containing matrix with all drug dosages => let's do feature preselection
   tmp_mat <- tmp_row$drug_feature_matrices[[1]]
   tmp_mat <- feature_selection_variance(tmp_mat, featStart = 3, percentTop = v)
   tmp_row$drug_feature_matrices[[1]] <- tmp_mat # replace the matrix
   tmp_row$feat_preselect <- paste0("top", v, "pct") # update metadata
   matrix_container <- bind_rows(matrix_container, tmp_row) # and update our data container
}

# repeat the same thing with the table that doesn't have all dosages but only those dosages with 
# most interactions in the chemical genomics data
# I know, code repetition - shame! but I really want to be explicit here
(targetrow <- match("most_interactions", matrix_container$drug_dosages))
for (v in variances_to_select) {
   tmp_row <- matrix_container[targetrow, ] # = row containing matrix with all drug dosages => let's do feature preselection
   tmp_mat <- tmp_row$drug_feature_matrices[[1]]
   tmp_mat <- feature_selection_variance(tmp_mat, featStart = 3, percentTop = v)
   tmp_row$drug_feature_matrices[[1]] <- tmp_mat # replace the matrix
   tmp_row$feat_preselect <- paste0("top", v, "pct") # update metadata
   matrix_container <- bind_rows(matrix_container, tmp_row) # and update our data container
}
```

### Adding chemical features

Don't use all chemical features from KNIME. Make tables with and without chemical features

```{r}
# check if all drugs in all tables are in our 'drugs_full' table
stopifnot(
   all(
      unique(flatten_chr(map(matrix_container$drug_feature_matrices, "drugname_typaslab")))
      %in%
      drugs_full$drugname_typaslab
   )
)

drugs_full_selected_features <- drugs_full[, c("drugname_typaslab", "SlogP", "LabuteASA", "TPSA", 
                                               "ExactMW", "NumLipinskiHBA", "NumLipinskiHBD", 
                                               "NumRotatableBonds", "NumAmideBonds", 
                                               "NumRings", "NumAromaticRings", "NumSaturatedRings", 
                                               "NumAliphaticRings", "data_effective_rotor_count")]

# take whole matrix_container, add chemical features, update metadata and rbind to old container
matrix_container <- 
   matrix_container %>%
   mutate(drug_feature_matrices = map(drug_feature_matrices, left_join, drugs_full_selected_features), 
          chemical_feats = TRUE, 
          datasets_included = map(datasets_included, append, "knime")) %>%
   bind_rows(matrix_container) %>%
   arrange(drug_dosages, feat_preselect, chemical_feats)
```


## Adding drug classification = mode of action information, generate dfr with list columns

Remove drugs with label "unknown", reducing the number of drugs from 83 to 78. 

```{r}
my_labels <- drugs_full[, c("drugname_typaslab", "process_broad")]
my_labels_knowndrugs <- my_labels[my_labels$process_broad != "unknown", ]

# remove unknown drugs, then add MoA information
matrix_container <- 
   matrix_container %>%
   mutate(drug_feature_matrices = map(drug_feature_matrices, semi_join, my_labels_knowndrugs)) %>%
   mutate(drug_feature_matrices = map(drug_feature_matrices, left_join, my_labels))

# arrange rows nicely
matrix_container$drug_feature_matrices <- 
   map(matrix_container$drug_feature_matrices, select, drugname_typaslab, conc, process_broad, everything())
```

## Adding model and hyperparameter specifications

For all of the above drug-feature matrices we want to run the following:
- random forests with a number of trees and mtry values
- boosted trees in 3 flavours: (i) 'normal' parameters changed, (ii) testing regularisation, (iii) 
  trying out subsample parameters
- lasso regression

```{r}
matrix_container.bak <- matrix_container
matrix_container_tmp <- matrix_container

# stuff common to all: tuning measures, CV instances
# normal instanced repeated stratified CV 
load("./data/programmatic_output/Rep_Nest_CV_instance_newDrugs.RData") 
# as above but with dosages blocked together
load("./data/programmatic_output/Rep_Nest_CV_instance_allDosage.RData") 

matrix_container$tuning_measure <- list("auc" = list(auc, mmce, ppv))
matrix_container$resamp_instance <- 
   ifelse(matrix_container$drug_dosages == "all", 
          list(Rep_Nest_CV_instance_allDosage), 
          list(Rep_Nest_CV_instance_newDrugs))

names(matrix_container$resamp_instance) <- # as ifelse ignores names
   ifelse(matrix_container$drug_dosages == "all", 
          "Rep_Nest_CV_instance_allDosage", 
          "Rep_Nest_CV_instance_newDrugs")


#####################################
## SPECIFYING HYPERPARAMETER GRIDS ##
#####################################
# specify hyperparameter grids, put them into lists with the fitted model as the names of the 
# elements
# lists should have same lengths as matrix_container since the whole matrix_container should be 
# processed once for each hyperparameter grid
# then apply some map magic to collect everything into a big data frame

#### step (1): specifying the hyperparameter grids

# RANDOM FORESTS:
rf_hyp_param <- 
   lapply(
      map_dbl(matrix_container$drug_feature_matrices, ncol), 
      function(x) {
         x <- x - 3 # to account for drugname, process_broad, conc
         makeParamSet(
            makeDiscreteParam("ntree", values = c(200, 500)), 
            makeDiscreteParam("mtry", values = floor(c(x, x*(3/4), x/2, x/4, sqrt(x))))
         )
      }
   )
names(rf_hyp_param) <- rep_len("rf_hyp_param", length(rf_hyp_param))

# XGBOOST:
# (a) 'standard' approach, tuning just most common parameters
xgboost_hyp_param_std <- 
   makeParamSet(
    makeDiscreteParam("nrounds", values = c(200,500)), # number of trees
    makeDiscreteParam("max_depth", values = c(1,2,3, 6)), 
    makeDiscreteParam("eta", values = c(0.01,0.1,0.3)) 
    )
xgboost_hyp_param_std <- rep(list("xgboost_hyp_param_std" = xgboost_hyp_param_std), nrow(matrix_container))

# (b) play around with regularisations
xgboost_hyp_param_reg <- 
   makeParamSet(
    makeDiscreteParam("nrounds", values = c(200,500)), # number of trees
    makeDiscreteParam("max_depth", values = c(1,2,3, 6)), 
    makeDiscreteParam("eta", values = c(0.01,0.1,0.3)), 
    makeDiscreteParam("lambda", values = c(1, 10, 100, 1000)), 
    makeDiscreteParam("alpha", values = c(0, 0.5, 1))
    )
xgboost_hyp_param_reg <- rep(list("xgboost_hyp_param_reg" = xgboost_hyp_param_reg), nrow(matrix_container))

# (c) play around with subsampling functions
xgboost_hyp_param_subsmp <- 
   makeParamSet(
    makeDiscreteParam("nrounds", values = c(200,500)), # number of trees
    makeDiscreteParam("max_depth", values = c(1,2,3, 6)), 
    makeDiscreteParam("eta", values = c(0.01,0.1,0.3)), 
    makeDiscreteParam("subsample", values = c(0.5, 0.8, 1)), 
    makeDiscreteParam("colsample_bytree", values = c(0.5, 0.8, 1))
    )
xgboost_hyp_param_subsmp <- rep(list("xgboost_hyp_param_subsmp" = xgboost_hyp_param_subsmp), nrow(matrix_container))

# LASSO:
lasso_hyp_param <- 
   makeParamSet(
      makeDiscreteParam("alpha", 1), 
      makeDiscreteParam("s", values = seq(from = 0.01, to = 10, length.out = 200))
   )
lasso_hyp_param <- rep(list("lasso_hyp_param" = lasso_hyp_param), nrow(matrix_container))


#### step (2): merging hyperparameter grids + model information with matrix_container

# add here the information about the model that is fitted
hyperparam_container <- 
   list("classif.randomForest" = rf_hyp_param, 
        "classif.xgboost" = xgboost_hyp_param_std, 
        "classif.xgboost" = xgboost_hyp_param_reg, 
        "classif.xgboost" = xgboost_hyp_param_subsmp, 
        "classif.glmnet" = lasso_hyp_param)

# turn into list of data frames
hyperparam_container <- 
   map2(hyperparam_container, 
        names(hyperparam_container), 
        ~data_frame('hyperparam_grid' = .x, 'fitted_model' = .y))

# dplyr functions remove names of list columns with map_dfr - so go back to good old do.call + rbind
matrix_container <- do.call(rbind, map(hyperparam_container, ~bind_cols(matrix_container, .x)))

saveRDS(matrix_container, file = "./data/programmatic_output/matrix_container.rds")
```

For convenience, save one copy of the_matrix with all dosages and one with most interactions (and 
keeping all genes = 'keepall', and no chemical features).

```{r}
tmp <- matrix_container$drug_feature_matrices[[1]]
saveRDS(object = tmp, file = "./data/programmatic_output/the_matrix_matrixcontainer_alldosg.rds")

tmp <- matrix_container$drug_feature_matrices[[91]]
saveRDS(object = tmp, file = "./data/programmatic_output/the_matrix_matrixcontainer_mostinteractions.rds")
```


# System and session info

```{r echo = TRUE, eval = TRUE}
R.version
sessionInfo()
```
