---
title: "Drugs chemical similarities"
author: "Florian Huber, Leonard Dubois"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

```{r setup}
knitr::opts_chunk$set(echo = T)
knitr::opts_chunk$set(message = T)
knitr::opts_chunk$set(warning = F)
knitr::opts_chunk$set(error = T)
knitr::opts_chunk$set(cache = F)
Sys.setlocale("LC_ALL", "en_IE.UTF-8")

library(tidyverse)
library(dendextend)

#Custom functions
walk(list.files("./R", pattern = "*.R", full.names = T), source)

load(file = "data/the_matrix_allDrugs.RData")

drugs_full <- read.table("/Volumes/typas/Florian/dbsetup_tables/drugs.csv", header = T, 
                         sep = ";", stringsAsFactors = F, dec = ".")

```


# Aim of the study

During model construction, some bias can be introduced based on two (or more) very similar drugs. If during the sampling these drugs are seperated beetween the test and training set, then one can argue that the model is tested with data it has already seen.

To prevent that, blocking can be introduced during the CV instances definition. Blocked individual are always in the same set.

For that, chemicla similarity beetween drugs must be computed. Here, fingerprints fom KNIME are used. These fingerprints use InChI (International Chemical Identifier)


# Export InChI in a file


```{r}

all_inchi = filter(drugs_full, drugname_typaslab %in% the_matrix_allDrugs$drugname_typaslab) %>% select(drugname_typaslab, data_stdinchi)
write_tsv(all_inchi, col_names = T, path = "data/all_inchi.tsv")

```


Then one only has to use again the KNIME workflow used for dbsetup construction. Just the input and output files have to be changed


# Read Fingerprint


```{r}

drugs_RDkit_fingerprint = read_csv2(file = "data/RDkit_fingerprint.csv")
drugs_RDkit_fingerprint = merge(all_inchi, drugs_RDkit_fingerprint, by = "data_stdinchi")
colnames(drugs_RDkit_fingerprint) = c("data_stdinchi", "drugnames_typaslab", "RDkit_fingerprint")

drugs_morgan_fingerprint = read_csv2(file = "data/morgan_fingerprint.csv")
drugs_morgan_fingerprint = merge(all_inchi, drugs_morgan_fingerprint, by = "data_stdinchi")
colnames(drugs_morgan_fingerprint) = c("data_stdinchi", "drugnames_typaslab", "RDkit_fingerprint")

drugs_MACCS_fingerprint = read_csv2(file = "data/MACCS_fingerprint.csv")
drugs_MACCS_fingerprint = merge(all_inchi, drugs_MACCS_fingerprint, by = "data_stdinchi")
colnames(drugs_MACCS_fingerprint) = c("data_stdinchi", "drugnames_typaslab", "RDkit_fingerprint")

```


```{r}

plot_dend = function(drugs_fingerprint, ...){
        
    fp_matrix = apply(drugs_fingerprint, 1,  function(x) {
                unlist(strsplit(x["RDkit_fingerprint"], split = "" ))
        }
    )
    fp_matrix = t(fp_matrix)
    rownames(fp_matrix) = drugs_fingerprint$drugnames_typaslab
    
    color_moa = c(rainbow(4), rep("black", 3))
    names(color_moa) = c("dna", "cell_wall", "membrane_stress", "protein_synthesis", "protein_qc", "oxidative_stress", "pmf")
    
    dist_fp_matrix = dist(fp_matrix, method = "binary")
    
    hclust_fp = hclust(dist_fp_matrix)
    dend_fp = as.dendrogram(hclust_fp, hang = 0.1)
    
    labels_colors(dend_fp) <- color_moa[the_matrix_allDrugs[order.dendrogram(dend_fp), "process_broad"]]
    par(mar = c(3,2,2,8)) 
    dend_fp %>%
        set("labels_cex", 0.7) %>%
        set("branches_lwd", 1.5) %>%
        plot(horiz = T, cex = 0.5, ...)
    
    abline(v = 0.1, lty = "dotted", lwd = 2, col ="darkgrey")
}

```


```{r}

plot_dend(drugs_fingerprint = drugs_RDkit_fingerprint, main = "Hclust of binary distance - RDKit fingerprint")
plot_dend(drugs_fingerprint = drugs_MACCS_fingerprint, main = "Hclust of binary distance - MACCS fingerprint")
plot_dend(drugs_fingerprint = drugs_morgan_fingerprint, main = "Hclust of binary distance - Morgan fingerprint")



```


# Analysis of the results

RDKit fingerprint shows more similarities beetween drugs, in particular, drugs with the same mode of action which are way too close (more than 90% chemical fingerprint similarities) are :

- Group 1 : Phleomycin and Bleomycin
- Group 2 : Tetracycline, Minocycline, Streptonigrin
- Group 3 : Actinomycin D, Vancomycin and mitomycin C
- Group 4 : Ampicillin and Carbenicillin

Groups 1 and 2 can also be linked together for the maximum difference beetween two of the five drugs from these groups is less than 10%


MACCS fingerprint also shows similarity beetween Minocycline and Tetracycline



# Drugs chemogenomic similarities


```{r}

chemgen_mat = select(the_matrix_allDrugs,  -process_broad, -drugname_typaslab)
#CecropinB is an outlier strongly influencing to final plot
rownames(chemgen_mat) = the_matrix_allDrugs$drugname_typaslab
chemgen_mat = chemgen_mat[-which(rownames(chemgen_mat) == "CECROPINB"), ]

dist_chemgen = dist(chemgen_mat, method = "euclidian")

color_moa = c(rainbow(4), rep("black", 3))
names(color_moa) = c("dna", "cell_wall", "membrane_stress", "protein_synthesis", "protein_qc", "oxidative_stress", "pmf")

hclust_chemgen = hclust(dist_chemgen, method = "complete")
dend_chemgen = as.dendrogram(hclust_chemgen, hang = 0.1)
    
labels_colors(dend_chemgen) <- color_moa[the_matrix_allDrugs[order.dendrogram(dend_chemgen), "process_broad"]]
par(mar = c(3,2,2,8)) 
dend_chemgen %>%
    set("labels_cex", 0.7) %>%
    set("branches_lwd", 1.5) %>%
    plot(horiz = T, cex = 0.5)

```
