---
title: ""
author: "Florian Huber, Leonard Dubois"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

# Setup, library loading

This part is the general setup, whichever model we are using.

```{r setup}
rm(list = ls())
# function to check if a package is installed, if so, load it, else install and then load it
source("./R/ipak.R")
# set chunk options and load libraries
source("./setup.R")
```


### *NEW CHUNK* 2018-08-10: inspecting data
One should probably check a bit the behaviour of our variables: how skewed are the distributions, 
are certain drugs or conditions far off, are NA values clustered in certain genes/drugs?


#### Predictor skewness

Let's check skewness of predictors first.

```{r}
skewness_vals <- sapply(the_matrix[, 3:ncol(the_matrix)], e1071::skewness, na.rm = TRUE)
skewness_vals <- data.frame(gene_synonym = names(skewness_vals), 
                            skewness = skewness_vals, 
                            stringsAsFactors = FALSE)

# indicate outlier boundaries using boxplot.stats
my_boundaries <- get_outlier_boundaries(skewness_vals$skewness)
skewness_vals$is_outlier <- 
   skewness_vals$skewness <= my_boundaries$lower_bound | 
   skewness_vals$skewness >= my_boundaries$upper_bound

my_lower <- my_boundaries$lower_bound
my_upper <- my_boundaries$upper_bound

ggplot(skewness_vals, aes(x = skewness)) + 
   geom_histogram(binwidth = 0.1) + 
   geom_vline(xintercept = c(my_lower, my_upper), linetype = "dotted") + 
   labs(title = "Skewness of predictors (mutants) across conditions\n(outliers indicated acc. to boxplot.stats())")

ggsave(filename = "./plots/NEW_predictor_skewness_distribution.pdf")
```

We have a number of predictors that are more skewed than the others: indicated by their skewness 
values again being outliers in the skewness distribution of all predictors.

```{r}
# skewness values are mostly negative, which makes sense, considering the nature of our data
# but there are 130 outliers
filter(skewness_vals, is_outlier) %>%
   arrange(skewness)
```

PLDA has the most negative skewness value, let's have a look:

```{r}
# a few seem to be quite bad, e.g. "PLDA"
hist(the_matrix$PLDA, breaks = 100, main = "Histogram of s-scores for PLDA")

pdf("./plots/NEW_PLDA_sscore_dist.pdf")
hist(the_matrix$PLDA, breaks = 100, main = "Histogram of s-scores for PLDA")
dev.off()
```

So actually it looks like a handful of genes with very low s-scores are responsible for the 
"skewness" of the distribution:

```{r}
e1071::skewness(the_matrix$PLDA)
my_boundaries <- get_outlier_boundaries(the_matrix$PLDA)
# skewness metric without outliers
e1071::skewness(my_boundaries$input_data_noout)
```

Interestingly, delta-PLDA seems to selectively interact with CHIR090. 3/4 of those interactions are 
statistically significant. Probably skewness is just one way of finding such "selective" genes. 

```{r}
dplyr::select(the_matrix, drugname_typaslab, conc, PLDA) %>%
   filter(PLDA <= my_boundaries$lower_bound)

# significant interactions:
dplyr::select(the_matrix_signifs, drugname_typaslab, conc, PLDA) %>%
   filter(PLDA)
```

Removing the outliers (according to `boxplot.stats()`) from each predictor makes the skewness 
distribution a lot more "normal":

```{r}
# what if we remove the outliers everywhere? 
skewness_vals$skewness_vals_noout <- 
   sapply(colnames(the_matrix[, 3:ncol(the_matrix)]), function(x) {
      noout <- get_outlier_boundaries(the_matrix[[x]])$input_data_noout
      return(e1071::skewness(noout, na.rm = TRUE))
})

my_boundaries <- get_outlier_boundaries(skewness_vals$skewness_vals_noout)
my_lower_new <- my_boundaries$lower_bound
my_upper_new <- my_boundaries$upper_bound

ggplot(skewness_vals, aes(x = skewness_vals_noout)) + 
   geom_histogram(binwidth = 0.1) + 
   geom_vline(xintercept = c(my_lower, my_upper), linetype = "dotted") + 
   geom_vline(xintercept = c(my_lower_new, my_upper_new), linetype = "dashed") + 
   labs(title = "Skewness of predictors (mutants) across conditions:
        \n(this time with outliers removed, dashed lines = new boundaries)")

ggsave("./plots/NEW_predictor_skewness_distribution_noout.pdf")
# seems like there are a few outliers left, perhaps worth checking them:
sort(boxplot.stats(skewness_vals$skewness_vals_noout)$out)

# let's have a look at the respective s-score histograms/boxplots, indicating the outliers
# skewness_vals$to_check <- skewness_vals$skewness_vals_noout < -1 | skewness_vals$skewness_vals_noout > 1
skewness_vals$to_check <- 
   skewness_vals$skewness_vals_noout <= my_lower_new | 
   skewness_vals$skewness_vals_noout >= my_upper_new

genes_to_check <- skewness_vals$gene_synonym[skewness_vals$to_check]
skewness_vals_melted <- 
   dplyr::select(the_matrix, drugname_typaslab, conc, genes_to_check) %>%
   gather(genes_to_check, key = "gene_synonym", value = "s_score") %>%
   left_join(skewness_vals[, c("gene_synonym", "skewness", "skewness_vals_noout")])

# add information about MoA:
moa_info <- drugs_full[, c("drugname_typaslab", "process_broad")]
moa_info$process_broad <- 
   ifelse(moa_info$process_broad %in% c("cell_wall", "dna", "protein_synthesis", "membrane_stress"), 
          moa_info$process_broad, 
          "other")

skewness_vals_melted <- left_join(skewness_vals_melted, moa_info)

annot_helper <- skewness_vals_melted %>%
   group_by(gene_synonym) %>%
   summarise(x = 0, y = 40, skewness = mean(skewness), skewness_vals_noout = mean(skewness_vals_noout))
```

These are the most skewed distributions after outlier removal. Some of them are really messed up, 
for example OXYR. 

```{r}
ggplot(skewness_vals_melted, aes(x = s_score)) + 
   geom_histogram() + 
   facet_wrap( ~ gene_synonym, scales = "free") + 
   geom_text(data = annot_helper, aes(label = round(skewness, digits = 2), x = x, y = y), color = "blue", size = 3)

ggsave(filename = "./plots/NEW_sscore_dists_skewed_features.pdf")
```

Pair plots of sscores of the skewed features. 

```{r}
all_by_all <- 
   full_join(skewness_vals_melted, skewness_vals_melted, 
             by = c("drugname_typaslab" = "drugname_typaslab", "conc" = "conc", "process_broad" = "process_broad"))

# plot_pairplots takes the data frame above and plots all by all combinations of the genes of 
# interest

plot_pairplots(c("PURD", "PURM"))
plot_pairplots(c("PURD", "PURM", "PYRE"))
```

Perhaps these are features that can be used to isolate certain (sub)groups of drugs? - would be 
interesting to test. Another interesting observation: s-scores can fluctuate a lot such as ACRA and 
novobiocin - why does conc = 6 suddenly have an s-score of 3.98? Is there a better way to select 
dosages than just highest concentrations or "most interactions"? In general, my impression was that 
s-scores _do_ go down with higher concentrations even though in an earlier analysis I couldn't see 
a clear trend. 

```{r}
filter(skewness_vals_melted, gene_synonym == "ACRA", drugname_typaslab == "NOVOBIOCIN")
dplyr::select(the_matrix_signifs, drugname_typaslab, conc, ACRA) %>%
   filter(drugname_typaslab == "NOVOBIOCIN", ACRA)
```


#### NA values

Are there drug-dosage combinations or mutants with an exceptional high number of NA values? 

Here, we can see that some genes have a high number of NA values. Perhaps they should be excluded. 
Not surprisingly, they are also all part of the "top10pct variance". Should probably fix in the 
future.

```{r}
the_matrix_melted <- 
   the_matrix %>% 
   gather(-one_of("drugname_typaslab", "conc"), key = "gene_synonym", value = "s_score")

the_matrix_melted_moainfo <- 
   left_join(the_matrix_melted, drugs_full[, c("drugname_typaslab", "process_broad")])
saveRDS(object = the_matrix_melted_moainfo, file = "./data/the_matrix_melted_moainfo.rds")

NAs_by_mutant <- 
   group_by(the_matrix_melted, gene_synonym) %>%
   summarise(total_conds = n(), total_conds_NA = sum(is.na(s_score)))

# and now the respective genes (seed arguments don't work)
set.seed(9)
ggplot(NAs_by_mutant, aes(x = "", y = total_conds_NA)) + 
   geom_text(aes(label = gene_synonym), size = 3, position = position_jitter(width = 0.3, height = 0)) + 
   geom_hline(yintercept = c(0, 5, 10, 15, 20, 30, 40), linetype = "dotted") + 
   theme_classic() + 
   scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 30, 40)) + 
   labs(title = "Number of conditions with 'NA' per mutant.\n(total number of conds = 256)")

ggsave("./plots/NEW_NA_conditions_per_mutant.pdf")
```

There are also some drug-dosage combinations with many NA values:

```{r}
NAs_by_drugndosg <- 
   group_by(the_matrix_melted, drugname_typaslab, conc) %>%
   summarise(total_conds = n(), total_conds_NA = sum(is.na(s_score)))

NAs_by_drugndosg$label <- paste(NAs_by_drugndosg$drugname_typaslab, NAs_by_drugndosg$conc, sep = "_")
ggplot(NAs_by_drugndosg, aes(x = "", y = total_conds_NA)) + 
   geom_text(aes(label = label), size = 3, position = position_jitter(width = 0.3)) + 
   labs(title = "Number of mutants with 'NA' per drug-dosage combination\n(total number of mutants = 1711)")

ggsave("./plots/NEW_NA_mutants_per_condition.pdf")
```


#### Significant values

How often are very low/very high s-scores significant?

Are NAs enriched at very low/high s_scores? Would probably have to look at s-score vs. concentration 
and see if NAs often occur after high/low s_scores. 

```{r}
the_matrix_signifs_melted <- 
   gather(the_matrix_signifs, -one_of("drugname_typaslab", "conc"), key = "gene_synonym", value = "significant")

the_matrix_melted <- 
   left_join(the_matrix_melted, the_matrix_signifs_melted)

# 925 NA values in total
sum(is.na(the_matrix_melted$s_score))

the_matrix_melted <- the_matrix_melted[complete.cases(the_matrix_melted), ]

quantile(the_matrix_melted$s_score, probs = c(0.05, 0.995), na.rm = TRUE)

ggplot(the_matrix_melted, aes(x = s_score)) + 
   geom_histogram(aes(fill = significant), binwidth = 0.1, position = "identity") + 
   geom_vline(xintercept = c(-4, -3, 3, 4), linetype = "dotted") + 
   coord_cartesian(xlim = c(-4.5, 4.5)) + 
   scale_x_continuous(breaks = seq(from = -4, to = 4, by = 1))

ggsave("./plots/NEW_relative_fractions_signif.pdf")
```


```{r}
# Few lines added to check the impact of replacing NA value and also their distribution across drugs dosages

the_matrix$nb_NA = apply(the_matrix, 1, function(x){sum(is.na(x))})
counting_NA = the_matrix %>% select(drugname_typaslab, conc, nb_NA)
counting_NA = counting_NA %>%  mutate(uniqueDrug = paste(drugname_typaslab, conc, sep = "_"))

matrix_container = readRDS(file = "data/matrix_container_new.rds")
dosages_used = matrix_container[1, ]$drug_feature_matrices[[1]] %>% select(drugname_typaslab, conc)
dosages_used = dosages_used %>% mutate(uniqueDrug = paste(drugname_typaslab, conc, sep = "_"))

counting_NA$used = counting_NA$uniqueDrug %in% dosages_used$uniqueDrug
counting_NA = counting_NA %>% select(-uniqueDrug)

boxplot(counting_NA$nb_NA ~ counting_NA$used)
# Not any significant difference

the_matrix = the_matrix %>% select(-nb_NA)
```