---
title: "Inspecting our data: skewness, NA values"
author: "Florian Huber"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

# Setup, library loading

This part is the general setup, whichever model we are using.

```{r setup}
rm(list = ls())
# function to check if a package is installed, if so, load it, else install and 
# then load it
source("./R/ipak.R")
# set chunk options and load libraries
source("./setup.R")
knitr::opts_chunk$set(cache = FALSE)
outdir <- "./data/programmatic_output"
```


# Understanding the data

One should probably check a bit the behaviour of our variables: how skewed are 
the distributions, are certain drugs or conditions far off, are NA values 
clustered in certain genes/drugs?

We will take the matrix after hypomorphic mutant selection and after removal of 
genes not interacting with any drug but before NA imputation, with all dosages, 
and before removal of different drugs.

```{r}
indir <- "./data/programmatic_output"
the_matrix <- readRDS(file.path(indir, "Inspecting_the_matrix_input.rds"))
drugs_complete <- readRDS(file.path(indir, "drugs_complete.rds"))
```

## Predictor skewness

Let's check skewness of predictors first.

```{r}
(the_matrix_signifs <- 
   select(the_matrix, gene_synonym, drugname_typaslab, conc, significant) %>%
   spread(key = gene_synonym, value = significant))

(the_matrix <- 
   select(the_matrix, gene_synonym, drugname_typaslab, conc, sscore) %>%
   spread(key = gene_synonym, value = sscore))

skewness_vals <- sapply(the_matrix[, 3:ncol(the_matrix)], e1071::skewness, 
  na.rm = TRUE)
(skewness_vals <- tibble(gene_synonym = names(skewness_vals), 
  skewness = skewness_vals))

# indicate outlier boundaries using boxplot.stats
my_boundaries <- get_outlier_boundaries(skewness_vals$skewness)
skewness_vals$is_outlier <- 
   skewness_vals$skewness <= my_boundaries$lower_bound | 
   skewness_vals$skewness >= my_boundaries$upper_bound

my_lower <- my_boundaries$lower_bound
my_upper <- my_boundaries$upper_bound

ggplot(skewness_vals, aes(x = skewness)) + 
   geom_histogram(binwidth = 0.1) + 
   geom_vline(xintercept = c(my_lower, my_upper), linetype = "dotted") + 
   labs(title = "Skewness of predictors (mutants) across conditions\n(outliers indicated acc. to boxplot.stats())")

ggsave(filename = "./plots/Predictor_skewness_distribution.pdf")
```

We have a number of predictors that are more skewed than the others: indicated by their skewness 
values again being outliers in the skewness distribution of all predictors.

```{r}
# skewness values are mostly negative, which makes sense, considering the nature of our data
# but there are 141 outliers
filter(skewness_vals, is_outlier) %>%
   arrange(skewness)

most_neg <- with(skewness_vals, gene_synonym[which.min(skewness)])
```

`r most_neg` has the most negative skewness value, let's have a look:

```{r}
# a few seem to be quite bad, e.g. "PLDA"
hist(the_matrix[[most_neg]], breaks = 100, main = paste0("Histogram of s-scores 
  for ", most_neg))

pdf(paste0("./plots/NEW_", most_neg, "_sscore_dist.pdf"))
hist(the_matrix[[most_neg]], breaks = 100, main = paste0("Histogram of s-scores 
  for ", most_neg))
dev.off()
```

It looks like a handful of conditions with very low s-scores might be responsible 
for the "skewness" of the distribution:

```{r}
e1071::skewness(the_matrix[[most_neg]], na.rm = TRUE)
my_boundaries <- get_outlier_boundaries(the_matrix$PLDA)
# skewness metric without outliers
e1071::skewness(my_boundaries$input_data_noout)
```

As an example, PLDA seems to selectively interact with CHIR090. 3/4 of those 
interactions are statistically significant. Probably skewness is just one way 
of finding such "selective" genes. 

```{r}
for_example <- "PLDA"
dplyr::select(the_matrix, drugname_typaslab, conc, !!for_example) %>%
   filter(!!sym(for_example) <= my_boundaries$lower_bound)

# significant interactions:
dplyr::select(the_matrix_signifs, drugname_typaslab, conc, !!for_example) %>%
   filter(!!sym(for_example))
```

Removing the outliers (according to `boxplot.stats()`) from each predictor 
makes the skewness distribution a lot more "normal":

```{r}
# remove for each gene those conditions that are considered outliers, then 
# recompute skewness
skewness_vals$skewness_vals_noout <- 
   sapply(colnames(the_matrix[, 3:ncol(the_matrix)]), function(x) {
      noout <- get_outlier_boundaries(the_matrix[[x]])$input_data_noout
      return(e1071::skewness(noout, na.rm = TRUE))
})

my_boundaries <- get_outlier_boundaries(skewness_vals$skewness_vals_noout)
my_lower_new <- my_boundaries$lower_bound
my_upper_new <- my_boundaries$upper_bound

ggplot(skewness_vals, aes(x = skewness_vals_noout)) + 
   geom_histogram(binwidth = 0.1) + 
   geom_vline(xintercept = c(my_lower, my_upper), linetype = "dotted") + 
   geom_vline(xintercept = c(my_lower_new, my_upper_new), linetype = "dashed") + 
   labs(title = "Skewness of predictors (mutants) across conditions:
        \n(this time with outliers removed, dashed lines = new boundaries)")

ggsave("./plots/Predictor_skewness_distribution_noout.pdf")
# seems like there are a few skewed conditions left, perhaps worth checking them:
sort(boxplot.stats(skewness_vals$skewness_vals_noout)$out)

# let's have a look at the respective s-score histograms/boxplots
skewness_vals$to_check <- 
   skewness_vals$skewness_vals_noout <= my_lower_new | 
   skewness_vals$skewness_vals_noout >= my_upper_new

(genes_to_check <- skewness_vals$gene_synonym[skewness_vals$to_check])
skewness_vals_melted <- 
   dplyr::select(the_matrix, drugname_typaslab, conc, genes_to_check) %>%
   gather(genes_to_check, key = "gene_synonym", value = "s_score") %>%
   left_join(skewness_vals[, c("gene_synonym", "skewness", "skewness_vals_noout")])

# add information about MoA:
moa_info <- drugs_complete[, c("drugname_typaslab", "process_broad")]
skewness_vals_melted <- left_join(skewness_vals_melted, moa_info)

annot_helper <- skewness_vals_melted %>%
   group_by(gene_synonym) %>%
   summarise(x = 0, y = 40, skewness = mean(skewness), 
     skewness_vals_noout = mean(skewness_vals_noout))
```

These are the most skewed distributions after outlier removal. Some of them are 
really messed up, for example OXYR. 

```{r}
ggplot(skewness_vals_melted, aes(x = s_score)) + 
   geom_histogram() + 
   facet_wrap( ~ gene_synonym, scales = "free") + 
   geom_text(data = annot_helper, aes(label = round(skewness, digits = 2), 
     x = x, y = y), color = "blue", size = 3)

ggsave(filename = "./plots/Sscore_dists_skewed_features.pdf", width = 12, 
  height = 12)
```

Pair plots of sscores of the skewed features. 

```{r}
all_by_all <- 
   full_join(skewness_vals_melted, skewness_vals_melted, 
     by = c("drugname_typaslab" = "drugname_typaslab", "conc" = "conc", 
       "process_broad" = "process_broad"))

# plot_pairplots takes the data frame above and plots all by all combinations of the genes of 
# interest

plot_pairplots(c("PURD", "PURM"))
plot_pairplots(c("PURD", "PURM", "PYRE"))
```

Perhaps these are features that can be used to isolate certain (sub)groups of 
drugs? - would be interesting to test. Another interesting observation: s-scores 
can fluctuate a lot such as ACRA and novobiocin - why does conc = 6 suddenly 
have an s-score of 3.98? Is there a better way to select dosages than just 
highest concentrations or "most interactions"? In general, my impression was 
that s-scores _do_ go down with higher concentrations even though in an earlier 
analysis I couldn't see a clear trend. 

```{r}
filter(skewness_vals_melted, gene_synonym == "ACRA", 
  drugname_typaslab == "NOVOBIOCIN")
dplyr::select(the_matrix_signifs, drugname_typaslab, conc, ACRA) %>%
   filter(drugname_typaslab == "NOVOBIOCIN", ACRA)
```


#### NA values

Are there drug-dosage combinations or mutants with an exceptional high number 
of NA values? 

Here, we can see that some genes have a high number of NA values. Perhaps they 
should be excluded. Not surprisingly, they are also all part of the 
"top10pct variance". Should probably fix in the future.

```{r}
the_matrix_melted <- 
   the_matrix %>% 
   gather(-one_of("drugname_typaslab", "conc"), key = "gene_synonym", 
     value = "s_score")

the_matrix_melted_moainfo <- 
   left_join(the_matrix_melted, 
     drugs_complete[, c("drugname_typaslab", "process_broad")])
# saveRDS(object = the_matrix_melted_moainfo, file = "./data/programmatic_output/the_matrix_melted_moainfo.rds")

(NAs_by_mutant <- 
   group_by(the_matrix_melted, gene_synonym) %>%
   summarise(total_conds = n(), total_conds_NA = sum(is.na(s_score))) %>%
   arrange(desc(total_conds_NA)))

# and now the respective genes (seed arguments don't work)
set.seed(9)
nconds <- unique(NAs_by_mutant$total_conds)
stopifnot(length(nconds) == 1)
ggplot(NAs_by_mutant, aes(x = "", y = total_conds_NA)) + 
   geom_text(aes(label = gene_synonym), size = 3, 
     position = position_jitter(width = 0.3, height = 0)) + 
   geom_hline(yintercept = c(0, 5, 10, 15, 20, 30, 40), linetype = "dotted") + 
   theme_classic() + 
   scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 30, 40)) + 
   labs(title = paste0("Number of conditions with 'NA' per mutant.
     (total number of conds = ", nconds, ")"))

(feats_to_remove <- NAs_by_mutant$gene_synonym[NAs_by_mutant$total_conds_NA > 10])
saveRDS(feats_to_remove, file.path(outdir, "feats_to_remove_many_NAs.rds"))

ggsave("./plots/NA_conditions_per_mutant.pdf")
```

There are also some drug-dosage combinations with many NA values:

```{r}
NAs_by_drugndosg <- 
   group_by(the_matrix_melted, drugname_typaslab, conc) %>%
   summarise(total_conds = n(), total_conds_NA = sum(is.na(s_score)))

NAs_by_drugndosg$label <- paste(NAs_by_drugndosg$drugname_typaslab, 
  NAs_by_drugndosg$conc, sep = "_")

ggplot(NAs_by_drugndosg, aes(x = "", y = total_conds_NA)) + 
   geom_text(aes(label = label), size = 3, 
     position = position_jitter(width = 0.3)) + 
   labs(title = paste("Number of mutants with 'NA' per drug-dosage combination 
     (total number of mutants =", NAs_by_drugndosg$total_conds[1], ")"))

ggsave("./plots/NA_mutants_per_condition.pdf")
```


#### Significant values

How often are very low/very high s-scores significant?

Are NAs enriched at very low/high s_scores? Would probably have to look at s-score vs. concentration 
and see if NAs often occur after high/low s_scores. 

```{r}
the_matrix_signifs_melted <- 
   gather(the_matrix_signifs, -one_of("drugname_typaslab", "conc"), 
     key = "gene_synonym", value = "significant")

the_matrix_melted <- left_join(the_matrix_melted, the_matrix_signifs_melted)

# 925 NA values in total
sum(is.na(the_matrix_melted$s_score))

the_matrix_melted <- the_matrix_melted[complete.cases(the_matrix_melted), ]

quantile(the_matrix_melted$s_score, probs = c(0.05, 0.995), na.rm = TRUE)

ggplot(the_matrix_melted, aes(x = s_score)) + 
   geom_histogram(aes(fill = significant), binwidth = 0.1, position = "stack") + 
   geom_vline(xintercept = c(-4, -3, 3, 4), linetype = "dotted") + 
   coord_cartesian(xlim = c(-4.5, 4.5)) + 
   scale_x_continuous(breaks = seq(from = -4, to = 4, by = 1))

ggsave("./plots/Relative_fractions_signif.pdf")
```


```{r, eval = FALSE, echo = FALSE}
#### NOTE 2019-01-21: probably not needed anymore

# check if there is a bias of NA values being more present in the dosage used by 'most interactions'
the_matrix$nb_NA = apply(the_matrix, 1, function(x){sum(is.na(x))})
counting_NA = 
   select(the_matrix, drugname_typaslab, conc, nb_NA) %>% 
   mutate(uniqueDrug = paste(drugname_typaslab, conc, sep = "_"))

matrix_container <- readRDS(file = "./data/programmatic_output/matrix_container.rds")
tmp <- 
   filter(matrix_container, drug_dosages == "most_interactions", feat_preselect == "keepall", 
          fitted_model == "classif.randomForest", !chemical_feats)[["drug_feature_matrices"]][[1]]
counting_NA$is_most_ia <- counting_NA$uniqueDrug %in% paste(tmp$drugname_typaslab, tmp$conc, sep = "_")

ggplot(counting_NA, aes(x = nb_NA)) + 
   geom_histogram(aes(fill = is_most_ia, y = ..density..), position = "identity", alpha = 0.5, 
     binwidth = 1)

# so there seems to be a slight trend but probably not important
```


```{r, session_info}
R.version
sessionInfo()
```

