---
title: ""
author: "Florian Huber"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

# Setup

```{r setup}
source("./setup.R")
```


Get feature importances from retrained model. 

```{r}
mod <- readRDS(file = "./data/programmatic_output/trained_model.rds")

# getFeatureImportance(mod)$res is a 1-row data frame with each column being 
# a gene
mod_imp <- gather(getFeatureImportance(mod)$res, key = "gene", value = "imp", 
  everything()) %>%
  filter(imp != 0) %>%
  arrange(desc(imp)) %>% 
  mutate(gene = fct_reorder(gene, imp), log2imp = log2(imp)) %>%
  as_tibble()

mod_imp
```

Showing it on a linear scale doesn't help much. The following plot suggests 
some "jumps" in the feature importance but this could be just by chance. One 
could take these "blocks" as cutoff for the fingerprint:

  * block 1: 4 genes
  * block 2: 5 genes
  * block 3: 12 genes
  * block 4: 13 genes
  * block 5: 14 genes

```{r, fig.height = 8}
ggplot(mod_imp[1:75, ], aes(x = log2(imp), y = gene)) + 
  geom_point()
```

Take, say, the first 4 blocks for the fingerprint = 34 genes: 

```{r}
ggplot(mod_imp[1:34, ], aes(x = log2(imp), y = gene)) + 
  geom_point()

fingerprint_mcl <- as.character(mod_imp$gene[1:34])
saveRDS(fingerprint_mcl, file = "./data/programmatic_output/fingerprint_mcl.rds")
```

tSNE map:

```{r}
m_all <- readRDS("./data/programmatic_output/m_all.rds")
tsne_mat <- select(m_all, drugname_typaslab, conc, process_broad, fingerprint_mcl)
tsne_mat$process_broad <- factor(tsne_mat$process_broad)
set.seed(5)
tsne_res <- Rtsne::Rtsne(X = tsne_mat[, -c(1:3)], dims = 3, perplexity = 10, 
  max_iter = 6000)

plotData <- data.frame(tsne_res$Y, MoA = tsne_mat$process_broad, 
  drug = paste0(tsne_mat$drugname_typaslab, "_", tsne_mat$conc))
colnames(plotData)[1:3] <- c("tSNE1", "tSNE2", "tSNE3")

p <- plot_ly(plotData, x = ~tSNE1, y = ~tSNE2, z = ~tSNE3, color = ~MoA, 
  colors = moa_cols[levels(tsne_mat$process_broad)], 
  marker = list(size = 8, line = list(color = 'rgba(0, 0, 0, 1)', 
    width = 1.5))) %>%
  add_markers(text = ~ drug) %>%
  layout(title = "Fingerprint tSNE map", 
    scene = list(xaxis = list(title = 'tSNE1'), yaxis = list(title = 'tSNE2'), 
      zaxis = list(title = 'tSNE3')))
p

saveRDS(object = p, file = "./data/programmatic_output/tSNE_fingerprint.rds")
```



# Session info

```{r session_info}
R.version
sessionInfo()
```

