---
title: "Miscellaneous analyses"
author: "Florian Huber, Leonard Dubois"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

# Setup, library loading

This part is the general setup, whichever model we are using.

```{r setup}
# function to check if a package is installed, if so, load it, else install and then load it
source("./R/ipak.R")
# set chunk options and load libraries
source("./setup.R")
# custom functions
walk(list.files("./R", pattern = "*.R", full.names = T), source)
load("./data/matrix_container.RData")

library(gridExtra)
```

# Hierarchical clusterings of drugs

## Chemical similarities

Check if some drugs are chemically very similar so that they may need to be blocked during CV 
instance creation. Use RDKit chemical fingerprints. Also compare hierarchical clusterings based 
on Nichols data (Euclidean distance and 1-correlation as distance).

Use InChI for KNIME workflow used during dbsetup construction, then calculate fingerprints. 

```{r}
the_matrix_allDrugs <- 
   filter(matrix_container, feat_preselect == "keepall", drug_dosages == "most_interactions", 
          chemical_feats == FALSE) %>%
   select(drug_feature_matrices) %>%
   unnest()

drugs_full <- read.table("/Volumes/typas/Florian/dbsetup_tables/drugs.csv", header = T, 
                         sep = ";", stringsAsFactors = F, dec = ".")

all_inchi <- 
   filter(drugs_full, drugname_typaslab %in% the_matrix_allDrugs$drugname_typaslab) %>% 
   select(drugname_typaslab, data_stdinchi)

write_tsv(all_inchi, col_names = T, path = "data/all_inchi.tsv")
```

Read fingerprints. 

```{r}
drugs_RDkit_fingerprint = read_csv2(file = "data/RDkit_fingerprint.csv")
drugs_RDkit_fingerprint = merge(all_inchi, drugs_RDkit_fingerprint, by = "data_stdinchi")
colnames(drugs_RDkit_fingerprint) = c("data_stdinchi", "drugnames_typaslab", "RDkit_fingerprint")
# could also get morgan and MACCS fingerprints, see ./data
```

Plot dendrogram of similarities. 

```{r}
library(gplots)
library(RColorBrewer)

cluster_matrix <- as.tibble(select(drugs_RDkit_fingerprint, -data_stdinchi))
row.names(cluster_matrix) <- cluster_matrix$drugnames_typaslab
cluster_matrix$drugnames_typaslab <- NULL
process_lut <- the_matrix_allDrugs$process_broad[match(row.names(cluster_matrix), the_matrix_allDrugs$drugname_typaslab)]
names(process_lut) <- row.names(cluster_matrix)

cluster_matrix <- as.matrix(cluster_matrix)
cluster_matrix_splitbits <- t(apply(cluster_matrix, 1, function(x) {
   as.numeric(unlist(strsplit(x["RDkit_fingerprint"], split = "")))
}))
cluster_matrix_splitbits_dist <- dist(cluster_matrix_splitbits, method = "binary")

moa_to_colour <- c(cell_wall = "#a6cee3",
                   dna = "#1f78b4",
                   protein_synthesis = "#b2df8a",
                   membrane_stress = "#33a02c",
                   pmf = "#bababa", protein_qc = "#bababa", oxidative_stress = "#bababa", 
                   unknown = "#bababa")
rowcols <- moa_to_colour[process_lut[rownames(cluster_matrix)]]

pdf("./plots/drug_drug_similarities_RDKit.pdf", width = 14, height = 14)
heatmap.2(cluster_matrix_splitbits, 
          trace = "none", 
          Rowv = as.dendrogram(hclust(cluster_matrix_dist)), 
          RowSideColors = rowcols, 
          margins = c(12, 9), 
          dendrogram = "row", 
          labCol = "", 
          breaks = c(0, 0.5, 1), 
          col = rev(heat.colors(n = 2)), 
          main = "Binary distances of drugs (RDKit fingerprint)")
legend("topright", 
       legend = names(moa_to_colour), 
       col = moa_to_colour, 
       lty = 1, 
       lwd = 5, 
       cex = 0.8)
dev.off()
```


PCA plot: most interactions, top 10% variance, no chemical features.

```{r}
m <- filter(matrix_container, feat_preselect == "top10pct", drug_dosages == "most_interactions", 
            chemical_feats == FALSE)$drug_feature_matrices[[1]]

m_matrix <- as.data.frame(m[, c(4:ncol(m))])
rownames(m_matrix) <- m$drugname_typaslab
pr.out <- prcomp(m_matrix, scale = TRUE)
prcomps <- as.data.frame(pr.out$x)
prcomps$drugname_typaslab <- row.names(prcomps)
prcomps <- left_join(prcomps, m[, c("drugname_typaslab", "process_broad")])
prcomps <- select(prcomps, drugname_typaslab, process_broad, everything())

prcomps$process_broad[!(prcomps$process_broad %in% c("cell_wall", "dna", "membrane_stress", "protein_synthesis"))] <- "other"
p1 <- ggplot(prcomps, aes(x = PC1, y = PC2)) + 
   geom_point(aes(colour = process_broad)) + 
#   geom_label_repel(aes(label = drugname_typaslab)) + 
   theme_bw() + 
   ggtitle("PCA (Nichols, top 10% var)")

p2 <- ggplot(prcomps, aes(x = PC1, y = PC3)) + 
   geom_point(aes(colour = process_broad)) + 
#   geom_label_repel(aes(label = drugname_typaslab)) + 
   theme_bw()

p3 <- ggplot(prcomps, aes(x = PC2, y = PC3)) + 
   geom_point(aes(colour = process_broad)) + 
#   geom_label_repel(aes(label = drugname_typaslab)) + 
   theme_bw()

p4 <- ggplot(prcomps, aes(x = PC3, y = PC4)) + 
   geom_point(aes(colour = process_broad)) + 
#   geom_label_repel(aes(label = drugname_typaslab)) + 
   theme_bw()

p <- grid.arrange(p1, p2, p3, p4, nrow = 2)
ggsave(p, file = "./plots/PCA_plots.pdf")

```




## Nichols data: Euclidean distance

<!--
include later (see FeatureImp_... notebook) when we have our big results object
-->



## Nichols data: (1 - Pearson) distance






