---
title: "MoA Prediction: the whole story"
author: "Florian Huber, Leonard Dubois"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

# Setup, library loading

This part is the general setup, whichever model we are using.

```{r setup}
# function to check if a package is installed, if so, load it, else install and then load it
source("./R/ipak.R")
# set chunk options and load libraries
source("./setup.R")
# custom functions
walk(list.files("./R", pattern = "*.R", full.names = T), source)
```


# Loading data and selecting features

```{r data_loading_feature_select, child = '1_DataLoading_FeaturePreselect.Rmd'}
```


# Instantiation of nested CV

```{r cv_instantiation, child = '0_Defining_sampling_instances.Rmd'}
```


# Miscellaneous

Stuff that's generally interesting - e.g. drug chemical similarities. 

```{r misc, child = 'Misc.Rmd'}
```


# Fitting models
<!--
description of model fitting procedure
-->


# Comparing performances

Generate ROC, precision-recall curves, influence of hyperparameters sets and other stuff for 
comparing which model is the "best". 

```{r comparing_performances, child = 'Comparing_performances.Rmd'}
```


# Inspecting models

To understand the different models such as which features are important etc. 

```{r inspecting_models, child = 'Inspecting_models.Rmd'}
```



