---
title: "Predicting drug MoA in Salmonella"
author: "Florian Huber"
date: "`r Sys.Date()`"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r}
source("./setup.R")
```


Mapping Nichols gene synonyms to current/modern annotation.

```{r}
(fpt <- readRDS("./data/programmatic_output/fpt.rds"))

id_map <- read_delim(file = "./data/All_genes_of_E._coli_K-12_substr._MG1655__ECOCYC_to_GENENAME.txt", 
                    delim = "\t")
colnames(id_map) <- c("gene_name_ecocyc", "ecocyc_id")

# this is a list of the genes in Nichols with their old names
(genes_nichols <- read_delim("./data/gene_list_nichols.csv", delim = ";"))
colnames(genes_nichols) <- c("ecocyc_id", "gene_synonym_nichols")

newnames <- left_join(genes_nichols, id_map) %>% 
  select(gene_synonym_nichols, ecocyc_id, gene_name_ecocyc)

# The following genes in nichols did not have a corresponding EcoCyc ID, sometimes 
# because the polypeptide is present in another strain, check, for example, ECK2652 
# in the Ecocyc Browser. 
(not_mapped <- newnames[is.na(newnames$gene_name_ecocyc), ])
# ECK1135 maps to both ymfN and aaaE, ymfN seems to be the correct name
# The following excludes all genes that are in "not_mapped" but it does not affect 
# the chemogenomic fingerprint
if (any(fpt %in% not_mapped$gene_synonym_nichols)) stop()

newnames <- filter(newnames, gene_name_ecocyc != "aaaE")
```

Map fingerprint genes to new annotations. 

```{r}
fpt_mapped <- fpt
# fix names
fpt_mapped[fpt_mapped == "PAL_and_4_more"] <- "PAL"
fpt_mapped[fpt_mapped == "LPCA_and_3_more"] <- "LPCA"
newnames_lut <- structure(newnames$gene_name_ecocyc, names = newnames$gene_synonym_nichols)
fpt_mapped <- newnames_lut[fpt_mapped]
fpt_mapped <- filter(newnames, gene_name_ecocyc %in% fpt_mapped)
```

Get Birgit's data on Salmonella before continuing. 

```{r}
# Apparently this is wrong:

# # Code taken from dbsetup:
# datadir <- '/Volumes/typas/Florian/chemical genomics data lab/STm/FINAL_DATA/scores/'
# # there is 'stm.corrpvalues.merged.txt' as well as 'stm.corrpvalues.original.txt' 
# # and 'stm.corrpvalues.purged.txt'
# qvals_birgit <- read.table(
#    file = paste(datadir, "pvalues_corrected", "stm.corrpvalues.purged.txt", sep = "/"), 
#    sep = "\t", header = T, stringsAsFactors = F)
# qvals_birgit <- as_tibble(qvals_birgit)
# qvals_birgit[1:10, 1:5]
# colnames(qvals_birgit)[1] <- "strain"
# hist(qvals_birgit$X4AMINOSALICYLICACID.10)
# 
# sscores_birgit <- read.table(
#    file = paste(datadir, "s-scores", "stm.scores.purged.txt", sep = "/"), 
#    sep = "\t", header = T, stringsAsFactors = F)
# sscores_birgit %<>% as_tibble()
# hist(sscores_birgit$AMIKACIN.0.05)
```

Not sure, Eli told me to use a different Salmonella table:

```{r}
sscores_st <- read_delim(file.path(datadir, "s-scores", "stm.scores.merged.txt"), delim = "\t")
colnames(sscores_st)[1] <- "Mutants"

qvals_st <- read_delim(file.path(datadir, "pvalues_corrected", "stm.corrpvalues.merged.txt"), delim = "\t")
colnames(qvals_st)[1] <- "Mutants"
```

In the Salmonella table the first column contains the locus tag in both STM14 and 
LT2, for example: STM14_0001-STM0001 (The latter part is the locus tag in LT2) followed 
by the two gene names in the 2 strains. Vlad parsed these names at least for some 
of the genes. 

And then there's some parsing/mapping that Vlad did (see also email from Feb 3rd, 2020; 
STM14 = locus tag for STM14028, STM for LT2): 

<!--
Hi Florian,
I’ve only resolved the names for genes that have at least one hit at FDR < 0.05 across any drug-concentration tuple (for the subset of 64 drugs overlapping with gram-negative screen)

In the end I split ST14 and STM identifiers (both of which are present in most cases) and I separately mapped ST14 and STM using Uniprot. I take (ST14 -> gene_symbol) as a reference and if there is nothing found I use the gene symbol from (LT2 -> gene_symbol) mapping. There are some cases for which neither LT2 nor 14028 has a gene symbol for that locus, in which case ST14 locus is retained.

Best regards,
Vlad
-->

```{r}
# So what's left to do for me is to split the locus tags myself
(st_vlad <- read_csv("./data/ST14028-gene-annot-uniprot.csv"))
```

Go back to the fingerprint file. We want to get the homologues for the fingerprint 
genes. 

When going to OMA, one gets a mapping of Uniprot IDs (E. coli) to SALT IDs (Salmonella). 

So first we need to map our fingerprint genes to Uniprot IDs. Nazgul generated a 
file mapping between Ecocyc IDs and Uniprot IDs:

```{r}
(ecoli_map <- read_delim("./data/EcoData_correctedECK.txt", delim = "\t"))
```


```{r}
# (1) --------
fpt_mapped2 <- left_join(fpt_mapped, ecoli_map[, c("ECK", "SP", "Gene")],
                         by = c("ecocyc_id" = "ECK"))
# sanity check
stopifnot(all(fpt_mapped2$gene_name_ecocyc == fpt_mapped2$Gene))
fpt_mapped2$Gene <- NULL
fpt_mapped2 <- rename(fpt_mapped2, uniprot = SP)
fpt_mapped2$uniprot[fpt_mapped2$uniprot == "Null"] <- NA

# only ohsC, which is a small RNA, could not be mapped to a Uniprot ID
print(fpt_mapped2, n = 30)
```

Now we can use the output of OMA to map E. coli Uniprot IDs (from the fingerprint) 
to the Salmonella homologues. Check file `./data/oma-uniprot.txt` (by Nazgul). SALT 
ID is in the first column, Uniprot in the second.

```{r}
# (2) --------
# This file contains the orthology mapping from the OMA browser, uniprot is 
# E. coli K12, salt_id is for Salmonella STM14028
(orthos <- read_tsv("./data/oma_mapping_EcoliK12_to_STM14028.tsv"))
orthos$noidea <- NULL

# now match to fpt_mapped2
fpt_mapped3 <- left_join(fpt_mapped2, orthos)
# we lose one more gene: fimF 
# and we have a 1:3 mapping for stfR
print(fpt_mapped3, n = 30)

# At this step we need to convert salt_id to uniprot
# Since the oma-uniprot file is huge (225 MB), do grep first
# not run (was run in terminal)
tmp <- paste0(fpt_mapped3$salt_id[!is.na(fpt_mapped3$salt_id)], collapse = "|")
write(x = tmp, file = "./data/salt_ids.txt")
# grep the file, then read in the output - wanted to use a bash script but had trouble 
# reading in pattern from file
# grep -e "SALT102521|SALT100833|SALT102099|SALT100154|SALT104900|SALT102118|SALT104823|SALT100516|SALT100484|SALT102070|SALT100351|SALT100224|SALT103380|SALT100766|SALT100842|SALT103828|SALT103287|SALT103477|SALT104355|SALT105300|SALT101147|SALT101413|SALT103054|SALT100217|SALT101333" ./data/oma-uniprot.txt > ./data/salt_ids_to_uniprot.tsv

salt_to_uniprot <- read_delim("./data/salt_ids_to_uniprot.tsv", delim = "\t", 
                              col_names = c("salt_id", "uniprot"))
fpt_mapped4 <- left_join(fpt_mapped3, salt_to_uniprot, by = "salt_id", 
                         suffix = c("", ".st"))
print(fpt_mapped4, n = 40)
```

To convert Uniprot IDs to gene names: can download a table from Uniprot that does 
the mapping. I saved it in `./data/uniprot_to_gene_Salmonella_STM14028.csv`.

```{r}
st_uniprot <- read_delim("./data/uniprot_to_gene_Salmonella_STM14028.csv", 
                         delim = "\t")
st_uniprot
fpt_mapped5 <- left_join(fpt_mapped4, st_uniprot[, c("Entry", "Gene names")], 
                         by = c("uniprot.st" = "Entry"))
```

What is left to do now is to map the Salmonella genes to the corresponding entry 
in Birgit's table. And then we can start predicting.

```{r}
# extract locus tag from fpt_mapped5 
# then grep corresponding entry in Birgit's table? 

# first match rows, then match conditions
# keep indices to get also the p values
fpt_mapped5$locustags <- str_extract(fpt_mapped5$`Gene names`, pattern = "STM14_\\d{3,4}")
fpt_mapped5$row_ind <- map_dbl(fpt_mapped5$locustags, function(x) {
  if (is.na(x)) {
    NA
  } else {
    res <- grep(pattern = x, x = sscores_st$Mutants)
    if (length(res) == 0) NA else res
  }
})

# Problem: ispA, lolB, gmhA, mutS, nagA, rbfA, and one of the stfR variants could 
# not be mapped
# (in addition to ryfC and fimf before)
grep(x = sscores_st, pattern = "ispA|lolB|gmhA|mutS|nagA|rbfA|stfR")

# in E. Coli:
# essential: ispA, lolB, 
# not essential: gmhA, mutS, nagA
# essentiality unclear: rbfA

# for gmhA (= lpcA) there is a homologue (STM14_3948) but we could also use one of the other 
# cluster genes 
# ispA, lolB, nagA, mutS - they are among the 9 genes with the least importance, also ryfC and fimF are low in importance
# only rbfA is a problem
```

Extract conditions that is in either Nichols' or Lucia's data. 

```{r}
indir <- "/Volumes/typas/Florian/dbsetup_tables_new"

(nichols_2011 <- read_delim(file.path(indir, "nichols_2011.csv"), delim = ";"))
(newsize <- read_delim(file.path(indir, "newsize.csv"), delim = ";"))
```

```{r}
conds_st <- colnames(sscores_st)[-1]
conds_ecoli <- unique(c(nichols_2011$drugname_typaslab, newsize$drugname_typaslab))
# conds_st_kept <- grep(x = conds_st, pattern = paste0(conds_ecoli, collapse = "|"), value = TRUE)
conds_st_split <- str_split(string = conds_st, pattern = "-")

# make sure everything's split into 2
stopifnot(str_split(string = conds_st, pattern = "-") %>% map_dbl(length) %>% `==`(2) %>% all())

conds_st_df <- tibble(orgnl_name = conds_st, 
                      drugname_typaslab = map_chr(conds_st_split, 1), 
                      conc = map_chr(conds_st_split, 2))
# there is also "TOBRAMYCIN-0.1.1"? - remove
conds_st_df %<>% filter(orgnl_name != "TOBRAMYCIN-0.1.1")
conds_st_df$conc %<>% parse_number()
View(conds_st_df)
# now keep only conditions that we already had in E. coli
conds_st_df_filt <- filter(conds_st_df, drugname_typaslab %in% conds_ecoli) %>% 
  arrange(drugname_typaslab)
View(conds_st_df_filt)
```

Predictions: Initial attempt. 

```{r}
# First, reduce the Salmonella matrix to the drugs we have in Nichols/Lucia as well 
# as the mapped orthologues. 
dfm_st <- sscores_st[na.omit(fpt_mapped5$row_ind), conds_st_df_filt$orgnl_name]
dfm_st <- bind_cols(sscores_st[na.omit(fpt_mapped5$row_ind), "Mutants", drop = FALSE], 
                    dfm_st)

# check multiple presence of stfr (fpt_mapped5[c(23, 25), ])
# impute NA values (how?)
dfm_st <- gather(dfm_st, 2:last_col(), key = "cond_orgnl_name", value = "sscore")
# resolve condition information
dfm_st <- left_join(dfm_st, conds_st_df_filt, by = c("cond_orgnl_name" = "orgnl_name")) %>% 
  select(-cond_orgnl_name)

# Table to map mutants to the corresponding orthologous Nichols gene - this is needed 
# to make predictions work.

mut_to_nic <- select(dfm_st, Mutants) %>% 
  distinct() %>% 
  mutate(locustags = str_extract(string = Mutants, pattern = "STM14_\\d{3,4}")) %>% 
  left_join(fpt_mapped5[, c("locustags", "gene_synonym_nichols")])

# resolve issue with stfr:
stfr <- filter(dfm_st, Mutants %in% c("STM14_1190-STM1049---", "STM14_3170-STM2588---"))
stfr <- spread(stfr, key = "Mutants", value = "sscore")

# Correlation is very poor between the two
plot(stfr$`STM14_1190-STM1049---`, stfr$`STM14_3170-STM2588---`)
cor(x = stfr$`STM14_1190-STM1049---`, y = stfr$`STM14_3170-STM2588---`, 
    use = "complete.obs")

# Correlation with the Nichols gene STFR
m_all <- readRDS("./data/programmatic_output/m_all.rds")

stfr <- left_join(stfr, m_all[, c("drugname_typaslab", "conc", "STFR")])
cor(x = stfr$`STM14_1190-STM1049---`, y = stfr$STFR, 
    use = "complete.obs")
cor(x = stfr$`STM14_3170-STM2588---`, y = stfr$STFR, 
    use = "complete.obs")
plot(x = stfr$`STM14_1190-STM1049---`, y = stfr$STFR)
plot(x = stfr$`STM14_3170-STM2588---`, y = stfr$STFR)

# Correlation with STM14_3170-STM2588--- looks more convincing - keep this one
dfm_st %<>% filter(Mutants != "STM14_1190-STM1049---")
dfm_st <- left_join(dfm_st, mut_to_nic)
dfm_st_long <- select(dfm_st, gene_synonym_nichols, drugname_typaslab, conc, sscore)
dfm_st_wide <- spread(dfm_st_long, key = "gene_synonym_nichols", value = "sscore")
```

Quick visual comparison of chemogenomic profile for the cell wall marker genes mrcB, 
slt, ycfM: concentrations in Birgit's screen were markedly lower in almost all cases - 
could be reason why it doesn't really look similar (except, partially, mecillinam). 






