---
title: "Production models, predictions, feature importances"
author: "Florian Huber"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

# Setup

```{r setup, message = FALSE}
source("./setup.R")
```

# A "production model" of MoA prediction

## Recap of previous findings

Nested cross-validation tells us the generalisation error estimate of the model 
tuning procedure in the inner loop. Using this generalisation error we found out 
that random forests, all drug dosages, no chemical features is the best set-up 
for an MoA classifier: 

```{r}
# get the data set
mc_ext <- readRDS("./data/programmatic_output/mc_ext.rds")

chosen <- filter(mc_ext, fitted_model == "classif.randomForest", 
  drug_dosages == "all", !chemical_feats)

perfs <- 
  chosen$perf_measures[[1]] %>%
  group_by(cvrep) %>%
  summarise(mean_mmce = mean(mmce))

cv_perf_cplt <- mean(perfs$mean_mmce)
```

This classifier had an average accuracy of `r 1 - mean(perfs$mean_mmce)`. 

```{r}
# overall performance: 70% accuracy 
perfs %>%
  ggplot(aes(x = "", y = mean_mmce)) + 
    geom_boxplot(outlier.shape = NA, width = 0.5) + 
    geom_point(position = position_jitter(width = 0.2, height = 0), shape = 1) + 
    labs(title = "Random forests, all dosages, no chem. features", x = "", 
      y = "Mean MMCE (one dot per nested CV)") + 
  comparison_theme

ggsave(filename = "./plots/Performance_RF_all.pdf", width = 87, height = 90, 
  units = "mm")

# our input data set (dfm = drug-feature matrix = same as m_all)
dfm <- chosen$drug_feature_matrices[[1]]

# cvinstance we will use for tuning:
rin <- chosen$resamp_instance[[1]][[1]]
```

## Retraining on the whole training dataset: complete model

To actually deploy our model we need to first tune the parameters, then train 
on the whole dataset (= routine of inner loop). Functions needed are in 
`fit_one_row.R`. 

### Tune parameters

```{r}
(lrn <- makeLearner(cl = chosen$fitted_model[1], predict.type = "prob"))
(lrn_wrapped <- makeFilterWrapper(learner = lrn, fw.method = "variance", 
  fw.perc = 0.05))

(tsk <- make_my_task(dfm = dfm, blockvar = "drugname_typaslab"))

sqrt_p <- floor(sqrt(ncol(dfm)))
rf_grid <- makeParamSet(
  makeDiscreteParam("ntree", values = c(200, 500, 1000)), 
  makeDiscreteParam("mtry", values = c(sqrt_p, sqrt_p + 25, sqrt_p + 50, 
    sqrt_p + 75, sqrt_p + 100)), 
  makeDiscreteParam("fw.perc", values = c(0.25, 0.5, 1))
)

(my_file <- "./data/programmatic_output/tuned_params_chosen.rds")
if (!file.exists(my_file)) {
  tuned_params <- tuneParams(learner = lrn_wrapped, task = tsk, resampling = rin, 
    measures = chosen$tuning_measure[[1]], par.set = rf_grid, 
    control = makeTuneControlGrid())
  saveRDS(object = tuned_params, file = my_file)
} else {
  tuned_params <- readRDS(my_file)
}
tuned_params
```

### Retrain with tuned parameters

```{r}
# set seed? 
# original model
(tuned_lrn <- setHyperPars(lrn_wrapped, par.vals = tuned_params$x))

# models with proximity matrices, local importances
(tuned_lrn_prox <- setHyperPars(lrn_wrapped, par.vals = tuned_params$x, 
  proximity = TRUE))
(tuned_lrn_loc <- setHyperPars(lrn_wrapped, par.vals = tuned_params$x, 
    proximity = TRUE, localImp = TRUE))

train_or_load <- function(tuned_learner, task, modelfile) {
  if (!file.exists(modelfile)) {
    message("Modelfile does not exist, training classifier.")
    trained_model <- mlr::train(learner = tuned_learner, task = task)
    saveRDS(object = trained_model, file = modelfile)
    return(trained_model)
  } else {
    message("Modelfile already present, loading from file.")
    return(readRDS(modelfile))
  }
}

trained_model <- train_or_load(tuned_learner = tuned_lrn, task = tsk, 
  modelfile = "./data/programmatic_output/trained_model.rds")

trained_model_prox <- train_or_load(tuned_learner = tuned_lrn_prox, task = tsk, 
  modelfile = "./data/programmatic_output/trained_model_prox.rds")

trained_model_loc <- train_or_load(tuned_learner = tuned_lrn_loc, task = tsk, 
  modelfile = "./data/programmatic_output/trained_model_locimp.rds")
```

### Predictions of the complete model

For each of control set, test set, and unknown MoA set run predictions, report 
performance (if applicable), and generate a prediction heatmap. See 
DataLoading notebook for set definitions.

```{r}
split_sets <- readRDS("./data/programmatic_output/split_sets.rds")

predict_my_set <- function(trained_model, newdata) {
  predictions <- predict(trained_model, newdata = as.data.frame(newdata))
  predictions$data <- as_tibble(
    cbind(newdata[, c("drugname_typaslab", "conc")], 
      as.data.frame(predictions))
  )
  return(predictions)
}
```

#### Control set

```{r}
identical_conds <- split_sets$control_set %>% 
  filter(origin == "newsize") %>% 
  filter(paste(drugname_typaslab, conc) %in% 
      paste(split_sets$training_set$drugname_typaslab, split_sets$training_set$conc))

control_preds <- predict_my_set(trained_model = trained_model, 
  newdata = identical_conds)
performance(control_preds)

print(control_preds$data, n = 500)

plot_mcl_probs_heatmap(melt_pred_data_mcl(control_preds$data), mics = mics, 
  printplot = FALSE, save = TRUE, file = "./plots/Pred_heatmap_controlset.pdf")
```

#### Test set

```{r}
test_preds <- predict_my_set(trained_model = trained_model, 
  newdata = split_sets$test_set)

(tst_perf_cplt <- performance(test_preds))

print(test_preds$data, n = 500)

plot_mcl_probs_heatmap(melt_pred_data_mcl(test_preds$data), mics = mics, 
  printplot = FALSE, save = TRUE, plot_width = 170, plot_height = 125, 
  file = "./plots/Pred_heatmap_testset.pdf")

# usage note:
# plot_mcl_probs_lines(melt_pred_data_mcl(test_preds$data), save = TRUE, 
#   printplot = FALSE, file = "./plots/Pred_lines_testset.pdf")
```

#### Unknown MoA set

```{r}
unknown_preds <- predict_my_set(trained_model = trained_model, 
  newdata = split_sets$unknown_moas)

print(unknown_preds$data, n = 500)

plot_mcl_probs_heatmap(melt_pred_data_mcl(unknown_preds$data), mics = mics, 
  printplot = FALSE, save = TRUE, file = "./plots/Pred_heatmap_unknown.pdf")
```


```{r, eval = FALSE, include = FALSE}
## FOR PAPER -------------
melted_pred_data <- melt_pred_data_mcl(unknown_preds$data)

tmp <- suppressMessages(left_join(melted_pred_data, mics))
tmp <- tmp %>%
  mutate(drug_conc = sprintf("%-19s %-5s %-5s", 
    Hmisc::capitalize(tolower(drugname_typaslab)), conc, mic_curated),
    prob.med.range = cut(prob.med, breaks = seq(from = 0, to = 1, by = 0.1),
      labels = c("0-10%", "10-20%", "20-30%", "30-40%", "40-50%", "50-60%",
        "60-70%", "70-80%", "80-90%", "90-100%")),
    drug_conc = factor(drug_conc,
      levels = unique(drug_conc[order(truth, drugname_typaslab, conc)])))

tmp$truth <- fct_recode(tmp$truth, "Annotated MoA: Cell Wall" = "cell_wall",
  "Annotated MoA: DNA" = "dna", "Annotated MoA: Membrane Stress" = "membrane_stress",
  "Annotated MoA: Protein Synthesis" = "protein_synthesis")

# indicate if the median probability (across CV repeats) is the highest among 
# the 4 MoAs
tmp <- group_by(tmp, drug_conc) %>%
  mutate(is_max = (prob.med) == max(prob.med))
tmp$geompoint <- ifelse(tmp$is_max, tmp$drug_conc, NA)
tmp$geompoint <- levels(tmp$drug_conc)[tmp$geompoint]

# cols <- RColorBrewer::brewer.pal(9, "BuPu")
# cols <- colorRampPalette(cols)(10)
cols <- RColorBrewer::brewer.pal(min(9, nlevels(tmp$prob.med.range)), "BuPu")
cols <- colorRampPalette(cols)(min(10, nlevels(tmp$prob.med.range)))

tmp <- ungroup(tmp)
tmp$drug_conc %<>% droplevels()
tmp$drug_conc <- fct_relevel(tmp$drug_conc, rev(levels(tmp$drug_conc)))

ggplot(tmp, aes(x = drug_conc, y = predicted_prob)) +
  geom_tile(aes(fill = prob.med.range)) +
  geom_point(aes(x = geompoint), size = 0.3) +
  scale_fill_manual("Probability", values = cols) +
  scale_y_discrete("MoA predicted", labels = moa_repl3) +
  scale_x_discrete("") +
  paper_theme +
  theme(axis.text.y = element_text(family = "Courier", size = 6)) +
  coord_flip()

ggsave("./plots/paper/Pred_heatmap_unknown.pdf", width = 120, height = 180, 
  units = "mm")

filter(tmp, drugname_typaslab %in% c("THIOLUTIN", "ISONIAZID")) %>% 
  ggplot(aes(x = predicted_prob, y = prob.med, colour = drugname_typaslab)) +
    geom_point(shape = 1) +
    geom_line(aes(group = drug_conc), size = 0.3) + 
    labs(y = "Prediction probability") + 
    scale_x_discrete("MoA", labels = moa_repl3) + 
    scale_colour_manual("", labels = c("Isoniazid", "Thiolutin"), 
      values = c("#377eb8", "#ff7f00")) +
    paper_theme + 
    theme(legend.position = c(0.75, 0.85), legend.background = element_blank())

ggsave("./plots/paper/Pred_lines_Fig5.pdf", width = 57, height = 50, 
  units = "mm")
```


### Complete model: feature importance scores

#### Global feature importance

```{r}
# getFeatureImportance(mod)$res is a 1-row data frame with each column being 
# a gene
# mod_imp <- 
#   gather(getFeatureImportance(trained_model)$res, key = "gene", value = "imp", 
#     everything()) %>%
#   filter(imp != 0) %>%
#   arrange(desc(imp)) %>% 
#   mutate(gene = fct_reorder(gene, imp, .desc = TRUE), log2imp = log2(imp)) %>%
#   as_tibble()

mod_imp <- 
  getFeatureImportance(trained_model)$res %>% 
  rename(gene = variable, imp = importance) %>% 
  filter(imp != 0) %>%
  arrange(desc(imp)) %>% 
  mutate(gene = fct_reorder(gene, imp, .desc = TRUE), log2imp = log2(imp)) %>%
  as_tibble()
  
mod_imp
```

General distribution.

```{r}
ggplot(mod_imp, aes(x = log2imp)) + 
  geom_histogram(bins = 45) + 
  comparison_theme + 
  labs(x = "Feature importance (log2)", y = "Count") + 
  theme(panel.grid = element_blank())

ggsave(filename = "./plots/Feature_importance_hist.pdf", width = 45, 
  height = 45, units = "mm")
```

```{r}
fadd <- mod_imp$log2imp[mod_imp$gene == "FADD"]
ulab <- mod_imp$log2imp[mod_imp$gene == "ULAB"]
cutoff <- fadd - abs(fadd - ulab) / 2

top50 <- mod_imp[1:50, ]
top50$colour <- ifelse(top50$log2imp > cutoff, "#ca0020", "black")

ggplot(top50, aes(x = gene, y = log2imp, colour = colour)) + 
  geom_point(size = 0.75) + 
  geom_hline(yintercept = cutoff, linetype = "dotted") + 
  labs(x = "Gene", y = "Feature importance (log2)") + 
  scale_colour_identity() + 
  paper_theme + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 4))

ggsave(filename = "./plots/paper/Feature_importance_top50.pdf", width = 115, 
  height = 70, units = "mm", useDingbats = FALSE)

fpt <- as.character(mod_imp$gene[mod_imp$log2imp > cutoff])

saveRDS(fpt, file = "./data/programmatic_output/fingerprint_mcl.rds")
write.table(x = fpt, row.names = FALSE, col.names = FALSE, 
  quote = FALSE, file = "./data/programmatic_output/fingerprint_mcl.csv")
```

Fingerprint features: GO term analysis.

```{r}
# generated previously, changed PAL_and_4_more --> PAL; 
# LPCA_and_3_more --> LPCA
fpt_ids <- read.table("./data/programmatic_output/fpt_ecocyc.tsv", 
  header = TRUE, stringsAsFactors = FALSE) %>% 
  as_tibble()

x <- fpt_ids$object_id
write.table(x, file = "./data/programmatic_output/fpt_ecocyc_ids.txt", 
  row.names = FALSE, col.names = FALSE, quote = FALSE)
```



```{r, include = FALSE, eval = FALSE}
## FOR POSTER ------------
mutate(mod_imp, above_thresh = log2imp >= cutoff) %>% 
  ggplot(aes(x = log2imp, fill = above_thresh)) + 
    geom_histogram(bins = 35) + 
    comparison_theme + 
    labs(x = "Log2 feature importance", y = "Count") + 
    scale_fill_manual(values = c("#404040", "#ca0020")) + 
    poster_theme + 
    theme(legend.position = "None")

ggsave(filename = "./plots/POSTER_histogram.pdf", width = 120, height = 110, 
  units = "mm")

## FOR PAPER ------
mutate(mod_imp, above_thresh = log2imp >= cutoff) %>% 
  ggplot(aes(x = log2imp, fill = above_thresh)) + 
    geom_histogram(bins = 35) + 
    comparison_theme + 
    labs(x = "Log2 feature importance", y = "Count") + 
    scale_fill_manual(values = c("#404040", "#ca0020")) + 
    paper_theme + 
    theme(legend.position = "None")

ggsave(filename = "./plots/paper/FeatImp_histogram.pdf", width = 50, height = 50, 
  units = "mm")
```

#### Local feature importances

Feature importances broken down by class. 

```{r}
# this here returns a matrix with all the features in the rows and the 
# importance for the MoAs in the columns:
imp <- trained_model_loc[["learner.model"]][["next.model"]][["learner.model"]][["importance"]]
imp <- as_tibble(imp, rownames = "gene")
imp

# break feature importance down into MoA
fpt_by_MoA <- filter(imp, gene %in% fpt)
fpt_by_MoA$total_imp <- apply(fpt_by_MoA[, 2:5], 1, sum)
fpt_by_MoA$gene <- factor(fpt_by_MoA$gene, 
  levels = fpt_by_MoA$gene[order(fpt_by_MoA$total_imp, decreasing = TRUE)])

fpt_by_MoA %>%
  select(gene:protein_synthesis) %>%
  gather(cell_wall:protein_synthesis, key = MoA, value = imp) %>%
  ggplot(aes(x = gene, y = imp)) + 
    geom_bar(aes(fill = MoA), stat = "identity") + 
    paper_theme + 
    labs(x = "Feature", y = "Feature importance by MoA") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) + 
    scale_fill_manual(labels = moa_repl, values = moa_cols)

ggsave(filename = "./plots/paper/Imp_by_MoA.pdf", width = 110, height = 70, 
  units = "mm")
```

Perhaps better to keep the features separated, makes it easier to see how some 
MoAs need only few features, others more features. 

```{r}
# alternatively: show difference in how many features are needed/how quickly 
# the feature importance drops:
tmp <- map_dfr(main_moas, function(.x) {
  .x <- ensym(.x)
  arrange(imp, desc(!!.x))[1:10, ] %>% 
    select(gene, !!.x) %>% 
    gather(!!.x, key = "MoA", value = "imp")
})

tmp$gene <- fct_inorder(tmp$gene)

ggplot(tmp, aes(x = gene, y = imp)) + 
  geom_bar(stat = "identity") + 
  facet_wrap( ~ MoA, ncol = 2, scales = "free") + 
  paper_theme + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave(filename = "./plots/top10each.pdf")
```

Case by case. 

```{r}
# this here returns a p by n matrix, the [i,j] element of which is the 
# importance of the i-th variable on the j-th case
loc_imp <- trained_model_loc[["learner.model"]][["next.model"]][["learner.model"]][["localImportance"]]
loc_imp <- as_tibble(loc_imp, rownames = "gene")

names(loc_imp)[2:ncol(loc_imp)] <- paste0(tsk$data_complete$drugname_typaslab, 
  "_", tsk$data_complete$conc)

filter(loc_imp, gene %in% c("SLT", "MRCB")) %>%
  select(gene, matches("CARBENICILLIN|A22"))
```

One can check which features were important for classifying which observation.

```{r}
# let's have a look how MRCB and SLT impact different drugs:
tmp <- 
  loc_imp %>%
  filter(gene %in% c("MRCB", "YCFM")) %>%
  gather(-gene, key = condition, value = loc_imp) %>%
  spread(key = gene, value = loc_imp) %>%
  mutate(process_broad = tsk$data_complete$process_broad[
    match(condition, paste0(tsk$data_complete$drugname_typaslab, "_", tsk$data_complete$conc))
  ])

tmp$condition_label <- ifelse(abs(tmp$MRCB) > 0.1 | abs(tmp$YCFM) > 0.1, tmp$condition, "")

ggplot(tmp, aes(x = MRCB, y = YCFM, colour = process_broad, label = condition_label)) + 
  geom_point() + 
  geom_text_repel(size = 3, vjust = 0, nudge_y = 0.001) + 
  scale_colour_manual(labels = moa_repl, values = moa_cols)

ggsave(filename = "./plots/LocalImp_MRCB_YCFM.pdf")


# RECC and RECA
tmp <- 
  loc_imp %>%
  filter(gene %in% c("RECC", "RECA")) %>%
  gather(-gene, key = condition, value = loc_imp) %>%
  spread(key = gene, value = loc_imp) %>%
  mutate(process_broad = tsk$data_complete$process_broad[
    match(condition, paste0(tsk$data_complete$drugname_typaslab, "_", tsk$data_complete$conc))
  ])

tmp$condition_label <- ifelse(
  (tmp$RECC > 0.05 | tmp$RECA > 0.04), tmp$condition, "")

filter(tmp, process_broad == "dna") %>% 
  ggplot(aes(x = RECC, y = RECA, colour = process_broad, label = condition_label)) + 
    geom_point() + 
    geom_text_repel(size = 3, vjust = 0, nudge_y = 0.001) + 
    scale_colour_manual(labels = moa_repl, values = moa_cols)

ggsave(filename = "./plots/LocalImp_RECC_RECA.pdf")
```


### Complete model: proximity matrix

Proximity scores. 

```{r}
proxmat <- trained_model_prox[["learner.model"]][["next.model"]][["learner.model"]][["proximity"]]
# how to get the data? - apparently we need the task 
row.names(proxmat) <- paste(tsk$data_complete$drugname_typaslab, 
  tsk$data_complete$conc, sep = "_")
colnames(proxmat) <- row.names(proxmat)

min_col <- plasma(2)[1]
max_col <- plasma(2)[2]

# Make annotation object
# ComplexHeatmap seems to have problems with tibbles! 
# use as.data.frame() because this function needs a factor
row_annot <- HeatmapAnnotation(df = as.data.frame(tsk$data_complete[, "process_broad"]), 
  col = list(process_broad = moa_cols), which = "row",
  name = "MoA", annotation_width = 3)

h <- Heatmap(matrix = proxmat,
  col = colorRamp2(breaks = c(0, 1), colors = c(min_col, max_col)),
  column_names_side = "top",
  row_names_side = "right",
  row_dend_side = "right",
  row_names_gp = gpar(fontsize = 7),
  column_names_gp = gpar(fontsize = 7),
  ) + row_annot

pdf(file = "./plots/proxmat.pdf", width = 20, height = 20)
print(h)
dev.off()


h <- Heatmap(matrix = proxmat,
  col = colorRamp2(breaks = c(0, 1), colors = c(min_col, max_col)),
  column_names_side = "top",
  row_names_side = "right",
  row_dend_side = "right",
  row_names_gp = gpar(fontsize = 7),
  column_names_gp = gpar(fontsize = 7),
  split = 5,
  column_split = 5, 
  ) + row_annot

pdf(file = "./plots/proxmat_split.pdf", width = 20, height = 20)
print(h)
dev.off()
```


## Retraining on the whole training dataset: parsimonious model

### Tune parameters

Only tune number of trees. 

```{r}
lrn_fpt <- makeLearner(cl = chosen$fitted_model[1], predict.type = "prob")

dfm_fpt <- dfm[, c("drugname_typaslab", "conc", "process_broad", fpt)]

tsk_fpt <- make_my_task(dfm = dfm_fpt, blockvar = "drugname_typaslab")

rf_grid_fpt <- makeParamSet(
  makeDiscreteParam("ntree", values = c(200, 500, 1000))
)

my_file <- "./data/programmatic_output/tuned_params_chosen_fpt.rds"
if (!file.exists(my_file)) {
  tuned_params_fpt <- tuneParams(learner = lrn_fpt, task = tsk_fpt, 
    resampling = rin, measures = chosen$tuning_measure[[1]], 
    par.set = rf_grid_fpt, control = makeTuneControlGrid())
  saveRDS(object = tuned_params_fpt, file = my_file)
} else {
  tuned_params_fpt <- readRDS(my_file)
}
```

Train model. 

```{r}
tuned_lrn_fpt <- setHyperPars(lrn_fpt, par.vals = tuned_params_fpt$x)

trained_model_fpt <- train_or_load(tuned_learner = tuned_lrn_fpt, task = tsk_fpt, 
  modelfile = "./data/programmatic_output/trained_model_fpt.rds")
```

### Predictions of the parsimonious model

#### Control set

```{r}
control_preds_pars <- predict_my_set(trained_model = trained_model_fpt, 
  newdata = split_sets$control_set)

performance(control_preds_pars)
# complete model:
performance(control_preds)

print(control_preds_pars$data, n = 500)

plot_mcl_probs_heatmap(melt_pred_data_mcl(control_preds_pars$data), mics = mics, 
  printplot = FALSE, save = TRUE, 
  file = "./plots/Pred_heatmap_controlset_parsimonious.pdf")
```

#### Test set

```{r}
test_preds_pars <- predict_my_set(trained_model = trained_model_fpt, 
  newdata = split_sets$test_set)

(tst_perf_pars <- performance(test_preds_pars))
# complete model:
performance(test_preds)

print(test_preds_pars$data, n = 500)

plot_mcl_probs_heatmap(melt_pred_data_mcl(test_preds_pars$data), mics = mics, 
  printplot = FALSE, save = TRUE, plot_width = 170, plot_height = 125, 
  file = "./plots/Pred_heatmap_testset_parsimonious.pdf")
```

#### Unknown MoA set

```{r}
unknown_preds <- predict_my_set(trained_model = trained_model_fpt, 
  newdata = split_sets$unknown_moas)

print(unknown_preds$data, n = 500)

plot_mcl_probs_heatmap(melt_pred_data_mcl(unknown_preds$data), mics = mics, 
  printplot = FALSE, save = TRUE, file = "./plots/Pred_heatmap_unknown_parsimonious.pdf")
```


```{r, eval = FALSE, include = FALSE}
## FOR PAPER
fig_4a <- tibble(
  which = c("Complete\nCV", "Complete\ntest", "Parsimonious\ntest"), 
  Accuracy = c(1 - cv_perf_cplt, 1 - tst_perf_cplt, 1 - tst_perf_pars)
)

ggplot(fig_4a, aes(x = which, y = Accuracy)) + 
  geom_bar(stat = "identity", width = 0.6, fill = "black") + 
  labs(x = "") + 
  paper_theme

ggsave(filename = "./plots/paper/Fig4_barplot.pdf", width = 45, height = 45, 
  units = "mm")

# correlation of prediction probabilities
test_preds
test_preds_pars

test_preds_m <- 
  select(test_preds$data, drugname_typaslab, conc, 
    prob.cell_wall:prob.protein_synthesis) %>% 
  gather(prob.cell_wall:prob.protein_synthesis, 
  key = "MoA", value = "prob")

test_preds_pars_m <- 
  select(test_preds_pars$data, drugname_typaslab, conc, 
    prob.cell_wall:prob.protein_synthesis) %>% 
  gather(prob.cell_wall:prob.protein_synthesis, 
  key = "MoA", value = "prob")

compare_preds <- full_join(test_preds_m, test_preds_pars_m, 
  by = c("drugname_typaslab", "conc", "MoA"), 
  suffix = c(".cplt", ".pars"))

ggplot(compare_preds, aes(x = prob.cplt, y = prob.pars)) + 
  geom_point(shape = 1, size = 0.75, alpha = 0.75) + 
  labs(x = "Probabilities complete", y = "Probabilities parsimonious") + 
  paper_theme

cor(compare_preds$prob.cplt, compare_preds$prob.pars, method = "pearson") ^ 2

ggsave("./plots/paper/Prob_corr_cplt_pars.pdf", width = 45, height = 45, 
  units = "mm")
```



# Clustering, dimensionality reduction

## tSNE

All features, training set.

```{r}
m_all <- readRDS("./data/programmatic_output/m_all.rds")
plot_tsne(m_all, save = TRUE, file = "./data/programmatic_output/tSNE_allfeats_training.rds")
```

Chemogenomic fingerprint, training set. 

```{r}
select(m_all, drugname_typaslab, conc, process_broad, fpt) %>%
  plot_tsne(save = TRUE, file = "./data/programmatic_output/tSNE_fingerprint_training.rds")
```

Chemogenomic fingerprint, all drugs (training set, test set, unknown drugs).  

```{r}
split_sets <- readRDS("./data/programmatic_output/split_sets.rds")
m_all_alldrugs <- bind_rows(split_sets$training_set, split_sets$test_set, 
  split_sets$unknown_moas)

select(m_all_alldrugs, drugname_typaslab, conc, process_broad, fpt) %>%
  plot_tsne(save = TRUE, file = "./data/programmatic_output/tSNE_fingerprint_alldrugs.rds")
```


```{r, include = FALSE, eval = FALSE}
## FOR POSTER --------------
tsne_mat <- m_all[, c("drugname_typaslab", "conc", "process_broad", fpt)]

tsne_mat$process_broad <- factor(tsne_mat$process_broad)
set.seed(5)

stopifnot(all(colnames(tsne_mat)[1:3] %in% c("drugname_typaslab", "conc", "process_broad")))

tsne_res <- Rtsne::Rtsne(X = tsne_mat[, -c(1:3)], dims = 3, perplexity = 25, 
  max_iter = 6000)

plotData <- data.frame(tsne_res$Y, MoA = tsne_mat$process_broad, 
  drug = paste0(tsne_mat$drugname_typaslab, "_", tsne_mat$conc))
colnames(plotData)[1:3] <- c("tSNE1", "tSNE2", "tSNE3")

p <- plot_ly(plotData, x = ~tSNE1, y = ~tSNE2, z = ~tSNE3, color = ~MoA, 
  colors = moa_cols[levels(tsne_mat$process_broad)], 
  marker = list(size = 8, line = list(color = 'rgba(0, 0, 0, 1)', 
    width = 1.5))) %>%
  add_markers(text = ~ drug) %>%
  layout(title = "tSNE map", 
    scene = list(xaxis = list(title = 'tSNE1'), yaxis = list(title = 'tSNE2'), 
      zaxis = list(title = 'tSNE3')))

p1 <- ggplot(plotData, aes(x = tSNE1, y = tSNE2, colour = MoA)) + 
    geom_point(alpha = 0.75) + 
    scale_colour_manual("MoA", values = moa_cols, labels = moa_repl) + 
    poster_theme + 
    theme(legend.position = "None")

p2 <- ggplot(plotData, aes(x = tSNE1, y = tSNE3, colour = MoA)) + 
    geom_point(alpha = 0.75) + 
    scale_colour_manual("MoA", values = moa_cols, labels = moa_repl) + 
    poster_theme

grid.arrange(p1, p2, ncol = 2, widths = c(unit(78, "mm"), unit(122, "mm")), 
  heights = unit(110, "mm")) %T>% 
  ggsave(filename = "./plots/POSTER_tSNE.pdf")


## FOR PAPER: Figure 3
fig3 <- ggplot(plotData, aes(x = tSNE1, y = tSNE2, colour = MoA)) + 
  geom_point(alpha = 0.75, shape = 16) + 
  scale_colour_manual("MoA", values = moa_cols, labels = moa_repl) + 
  paper_theme + 
  theme(legend.position = "None")

ggsave(plot = fig3, filename = "./plots/paper/tSNE1.pdf", width = 50, height = 50, 
  units = "mm")

fig3 + aes(x = tSNE1, y = tSNE3)

ggsave(filename = "./plots/paper/tSNE2.pdf", width = 50, height = 50, 
  units = "mm")

fig3 + aes(x = tSNE2, y = tSNE3)

ggsave(filename = "./plots/paper/tSNE3.pdf", width = 50, height = 50, 
  units = "mm")


## FOR PAPER: Figure S1
tsne_mat <- m_all

tsne_mat$process_broad <- factor(tsne_mat$process_broad)
set.seed(5)

stopifnot(all(colnames(tsne_mat)[1:3] %in% c("drugname_typaslab", "conc", "process_broad")))

tsne_res <- Rtsne::Rtsne(X = tsne_mat[, -c(1:3)], dims = 3, perplexity = 25, 
  max_iter = 6000)

plotData <- data.frame(tsne_res$Y, MoA = tsne_mat$process_broad, 
  drug = paste0(tsne_mat$drugname_typaslab, "_", tsne_mat$conc))
colnames(plotData)[1:3] <- c("tSNE1", "tSNE2", "tSNE3")

figS1 <- ggplot(plotData, aes(x = tSNE1, y = tSNE2, colour = MoA)) + 
  geom_point(alpha = 0.75, size = 0.75, shape = 16) + 
  scale_colour_manual("MoA", values = moa_cols, labels = moa_repl) + 
  paper_theme + 
  theme(legend.position = "None")

ggsave(plot = figS1, filename = "./plots/paper/FigS1_tSNE1.pdf", width = 50, height = 50, 
  units = "mm")

figS1 + aes(x = tSNE1, y = tSNE3)

ggsave(filename = "./plots/paper/FigS1_tSNE2.pdf", width = 50, height = 50, 
  units = "mm")

figS1+ aes(x = tSNE2, y = tSNE3)

ggsave(filename = "./plots/paper/FigS1_tSNE3.pdf", width = 50, height = 50, 
  units = "mm")


## FOR PAPER: Figure 5
split_sets <- readRDS("./data/programmatic_output/split_sets.rds")
m_train_unkn <- bind_rows(split_sets$training_set, split_sets$unknown_moas)

tsne_mat <- m_train_unkn[, c("drugname_typaslab", "conc", "process_broad", fpt)]
tsne_mat$process_broad <- factor(tsne_mat$process_broad)
set.seed(5)

stopifnot(all(colnames(tsne_mat)[1:3] %in% c("drugname_typaslab", "conc", "process_broad")))

tsne_res <- Rtsne::Rtsne(X = tsne_mat[, -c(1:3)], dims = 3, perplexity = 25, 
  max_iter = 6000)

plotData <- data.frame(tsne_res$Y, MoA = tsne_mat$process_broad, 
  drug = paste0(tsne_mat$drugname_typaslab, "_", tsne_mat$conc))
colnames(plotData)[1:3] <- c("tSNE1", "tSNE2", "tSNE3")

plotData$label <- ifelse(grepl(plotData$drug, pattern = "ISONIAZID|THIOLUTIN"), 
  as.character(plotData$drug), "")

fig5 <- ggplot(plotData, aes(x = tSNE1, y = tSNE2, colour = MoA, label = label)) + 
  geom_point(alpha = 0.75, size = 0.75, shape = 16) + 
  geom_text(size = 2, hjust = 0, vjust = 0, colour = "black") + 
  scale_colour_manual("MoA", values = moa_cols, labels = moa_repl) + 
  paper_theme + 
  theme(legend.position = "None")

ggsave(plot = fig5, filename = "./plots/paper/Fig5_tSNE1.pdf", width = 50, height = 50, 
  units = "mm")

fig5 + aes(x = tSNE1, y = tSNE3)

ggsave(filename = "./plots/paper/Fig5_tSNE2.pdf", width = 50, height = 50, 
  units = "mm")

fig5 + aes(x = tSNE2, y = tSNE3)

ggsave(filename = "./plots/paper/Fig5_tSNE3.pdf", width = 50, height = 50, 
  units = "mm")
```

## PCA

Also with fingerprint features on both training set and "all" drugs. 

```{r}
# all features, training set
plot_pca(m_all, save = TRUE, file = "./plots/PCA_allfeats_training.pdf")

# fingerprint features, training set
select(m_all, drugname_typaslab, conc, process_broad, fpt) %>% 
  plot_pca(save = TRUE, file = "./plots/PCA_fpt_training.pdf")

# fingerprint features, all drugs
select(m_all_alldrugs, drugname_typaslab, conc, process_broad, fpt) %>% 
  plot_pca(save = TRUE, file = "./plots/PCA_fpt_alldrugs.pdf")
```

## Hierarchical clustering

With fingerprint features, on the training set and on Nichols + Lucia + unknown 
drugs. 

```{r}
m_all <- readRDS("./data/programmatic_output/m_all.rds")
mode_of_action <- read_csv("./data/programmatic_output/drug_moa_userfriendly.csv")
mic_info <- read_delim("./data/programmatic_output/MICs.csv", delim = ";")

split_sets <- readRDS("./data/programmatic_output/split_sets.rds")
m_all_alldrugs <- bind_rows(split_sets$training_set, split_sets$test_set, 
  split_sets$unknown_moas)

# all features, training set
if (!file.exists("./plots/Hclust_allfeats_training.pdf")) {
  plot_heatmap(dfm = m_all, feats = colnames(select(m_all, AAEX:last_col())), 
    mics = mic_info, split = 4, 
    clustering_distance_rows = "spearman", 
    clustering_distance_columns = "spearman", 
    row_dend_side = "right", 
    plot_width = 45, plot_height = 15, 
    moa = mode_of_action, save = TRUE, file = "./plots/Hclust_allfeats_training.pdf")
}

# fingerprint features, training set
plot_heatmap(dfm = m_all, feats = fpt, mics = mic_info, split = 4,
  clustering_distance_rows = "spearman", 
  clustering_distance_columns = "spearman", 
  moa = mode_of_action, save = TRUE, file = "./plots/Hclust_fpt_training.pdf")

# fingerprint features, training set, split by MoA
walk(main_moas, function(moa) {
  filter(m_all, process_broad == moa) %>% 
    plot_heatmap(feats = fpt, mics = mic_info,
      clustering_distance_rows = "spearman", 
      cluster_rows = FALSE, 
      cluster_columns = FALSE, 
      moa = mode_of_action, 
      save = TRUE, 
      plot_height = 4.5, 
      plot_width = 3.4, 
      show_column_dend = FALSE, 
      show_heatmap_legend = FALSE, 
      show_legend = FALSE, 
      use_global_fpt_order = TRUE, 
      file = paste0("./plots/Hclust_fpt_training", moa, ".pdf"))
})

# fingerprint features, all drugs
plot_heatmap(dfm = m_all_alldrugs, 
             feats = fpt, mics = mic_info, 
             split = 4, 
             clustering_distance_columns = "spearman", 
             clustering_distance_rows = "spearman", 
             moa = mode_of_action, 
             cluster_columns = FALSE, 
             use_global_fpt_order = TRUE, 
             save = TRUE, 
             file = "./plots/Hclust_fpt_alldrugs.pdf")

```


```{r, include = FALSE, eval = FALSE}
## FOR PAPER (code adapted from plot_heatmap)

m <- m_all
feats <- colnames(select(m_all, AAEX:last_col()))
m <- suppressMessages(
  left_join(m, mode_of_action[, c("drugname_typaslab", "process_subgroup")]) %>%
  left_join(mics[, c("drugname_typaslab", "mic_curated")])
)
m <- arrange(m, process_broad, process_subgroup, drugname_typaslab)

dfr <- as.data.frame(m[, c("process_broad")])
rownames(m) <- paste0(m$drugname_typaslab, "_", m$conc, " (", 
  m$mic_curated, ")")

m <- select(m, -drugname_typaslab, -conc, -process_broad, -process_subgroup, 
  -mic_curated) %>%
  select(feats) %>% 
  as.matrix()

# Make annotation object
# ComplexHeatmap seems to have problems with tibbles! 
row_annot <- HeatmapAnnotation(df = dfr, 
  col = list(process_broad = moa_cols), which = "row", 
  name = "MoA", annotation_width = 3)
# row_annot
# draw(row_annot, 1:20)

my_distfun <- function(x, y) {1 - abs(cor(x, y))}
min_col <- plasma(2)[1]
max_col <- plasma(2)[2]

h <- Heatmap(matrix = m, 
  col = colorRamp2(breaks = c(-5, 5), colors = c(min_col, max_col)), 
  name = "S-score", 
  clustering_distance_rows = my_distfun, 
  clustering_distance_columns = my_distfun, 
  column_names_side = "top", 
  row_names_side = "right", 
  cluster_rows = TRUE, 
  row_dend_side = "right", 
  row_names_gp = gpar(fontsize = 4), 
  column_names_gp = gpar(fontsize = 5), 
  split = 4, 
#  cell_fun = function(j, i, x, y, width, height, fill) {
#    grid.text(sprintf("%.2f", m[i, j]), x, y, 
#      gp = gpar(col = "black", fontsize = 2))
#  }
) + row_annot
h <- h + rowAnnotation(rn = anno_text(rownames(m), gp = gpar(fontsize = 4)))

png(file = "./plots/paper/Figure_S1A_hclust.png")
print(h)
dev.off()


```


# Session info

```{r session_info}
R.version
sessionInfo()
```
